---
title: "CH1ManuscriptCode"
author: "Ana Silverio"
date: "2024-07-30"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
editor_options:
  chunk_output_type: console
always_allow_html: yes
---

# Manuscript titled: "Assessing the Resistance and Resilience of Important Recreational Fish Species to Extreme Events in Coastal Texas"

## Co-Authors: Ana C. Silverio, Mariah C. Livernois, Dakus Geeslin, Nathan Furey, and Easton R. White

The following is code for all figures and tables and respective calculations in the above mentioned manuscript submitted to AFS Marine and Coastal Fisheries on 11/11/2024. R Code for the calculations, figures and tables within the supplemental can be found in the separate file "Supp_MaterialCH1" in the repository. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, warning = FALSE, message = FALSE)

#Set working directory:
setwd("~/texas_extreme_events")

#Call in bag seines:
bag.seines <- read.csv("~/texas_extreme_events/Clean_TPWD_Data/UpdatedBagSeinesCondensed_CLEAN.csv") #This file is already cleaned from the raw data set recieved from TPWD. -> Ask if I should be including this code as well??

#Packages:
library(tidyverse)
library(lubridate)
library(knitr)
options(digits = 3)
library(ggforce)
library(tidyverse)
library("hrbrthemes")
library(viridis)
library(forcats)
library(ggpubr)
library(kableExtra)
library(magick)
library(webshot2)
library(xtable)

#color palette
colorBlindBlack8 <- c("#000000","#0072B2",  "#56B4E9","#009E73", "#F0E442", "#E69F00","#D55E00","#CC79A7")

#readable dates:
str(bag.seines)
bag.seines$DATE<- as.Date(bag.seines$DATE,
                                        format = "%m/%d/%y")

#adding the names of the bays into the data frame
bag.seines$MAJOR_AREA_CODE <- as.factor(bag.seines$MAJOR_AREA_CODE)

bag.seines <- bag.seines %>%  
  dplyr::mutate(MAJOR_AREA_CODE = recode(MAJOR_AREA_CODE, `1` = 'Sabine Lake', `2` = 'Galveston Bay', `3` = 'Matagorda Bay', `4` = 'San Antonio Bay', `5`= 'Aransas Bay', `6`='Corpus Christi Bay', `7`='Upper Laguna Madre', `8` = 'Lower Laguna Madre', `9`='East Matagorda Bay', `11` = 'Cedar Lakes'))

#removing bays that are not part of the analysis due to limited data points
bag.seines <- bag.seines %>% 
  filter(!(MAJOR_AREA_CODE == "Cedar Lakes")) %>% 
  filter(!(MAJOR_AREA_CODE == "East Matagorda Bay"))

##Plot theme
My_Theme <- theme(
  axis.title.x = element_text(size = 16),
  axis.text.x = element_text(size = 12),
  axis.title.y = element_text(size = 16),
  plot.title = element_text(size = 16),
  legend.text = element_text(size = 16),
  legend.title = element_text(size = 16),
  axis.ticks.length = unit(0.20, "cm"),
  axis.text.y = element_text(size = 12))



```

# Time series of each species 

```{r Monthly Analysis Calculations ONLY , include=FALSE}
#calculate monthly averages:
#adding the names of the bays into the data frame and making sure they are in the correct data type
bag.seines$MAJOR_AREA_CODE <- as.factor(bag.seines$MAJOR_AREA_CODE)


## Red drum Monthly Average Calculations -----
redDrum_mon_avg <- bag.seines %>%
  group_by(MONTH,YEAR,MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE))

redDrum_mon_avg <- redDrum_mon_avg %>%
  rename("CPUE_AvgRD" = "mean(rd_CPUE)")


# making column that combines month and year
redDrum_mon_avg$DAY <- 1
redDrum_mon_avg$MDY <- paste(redDrum_mon_avg$MONTH,redDrum_mon_avg$DAY, redDrum_mon_avg$YEAR, sep = "-")
redDrum_mon_avg$MDY <- as.Date(redDrum_mon_avg$MDY, format = "%m-%d-%Y")


## Spotted seatrout Calculation ------
sst_mon_avg <- bag.seines %>%
  group_by(MONTH,YEAR,MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE))

sst_mon_avg <- sst_mon_avg %>%
  rename("CPUE_AvgSST" = "mean(sst_CPUE)")

#sst_mon_avg$MAJOR_AREA_CODE <- as.character(sst_mon_avg$MAJOR_AREA_CODE)

#creating a data column for easier interpretation 
sst_mon_avg$DAY <- 1
sst_mon_avg$MDY <- paste(sst_mon_avg$MONTH,sst_mon_avg$DAY, sst_mon_avg$YEAR, sep = "-")
sst_mon_avg$MDY <- as.Date(sst_mon_avg$MDY, format = "%m-%d-%Y")


#Black drum calculation ---- 
blackDrum_mon_avg <- bag.seines %>%
  group_by(MONTH,YEAR,MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE))

blackDrum_mon_avg  <- blackDrum_mon_avg  %>%
  rename("CPUE_AvgBD" = "mean(bd_CPUE)")

blackDrum_mon_avg$MAJOR_AREA_CODE <- as.character(blackDrum_mon_avg$MAJOR_AREA_CODE)

## creating a data column
blackDrum_mon_avg$DAY <- 1
blackDrum_mon_avg$MDY <- paste(blackDrum_mon_avg$MONTH,blackDrum_mon_avg$DAY, blackDrum_mon_avg$YEAR, sep = "-")
blackDrum_mon_avg$MDY <- as.Date(blackDrum_mon_avg$MDY, format = "%m-%d-%Y")


## Southern Flounder calculation ----

SF_mon_avg <- bag.seines %>%
  group_by(MONTH,YEAR,MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE))

SF_mon_avg  <- SF_mon_avg %>%
  rename("CPUE_AvgSF" = "mean(sf_CPUE)")

SF_mon_avg$MAJOR_AREA_CODE <- as.character(SF_mon_avg$MAJOR_AREA_CODE)

#Creating a data column for easier plot interpretation
SF_mon_avg$DAY <- 1
SF_mon_avg$MDY <- paste(SF_mon_avg$MONTH,SF_mon_avg$DAY, SF_mon_avg$YEAR, sep = "-")
SF_mon_avg$MDY <- as.Date(SF_mon_avg$MDY, format = "%m-%d-%Y")




```

```{r Data Experiment 1 plots Hurricane Harvey, echo=FALSE}

## red drum plot
ggplot(data = redDrum_mon_avg %>% filter(YEAR > 2013), mapping = aes(x = MDY, y =  CPUE_AvgRD, color = MAJOR_AREA_CODE)) + geom_line(alpha = 0.8, size = 1) +  
geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000") + 
geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size=1, color = "#000000") +
theme_classic() + #facet_wrap(~MAJOR_AREA_CODE, scales = "free") +
   scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  labs(
  title = "Red Drum CPUE Monthly Average Since 2014",
  x = "Time",
  y = "CPUE (#/hectare)" 
) + theme(axis.text.x = element_text(angle=45, hjust=1))

## Saving the plots to my computer
#ggsave("RedDrum_Draft.jpg", width = 10, height = 8, units = c("in"), dpi = 300)


#spotted seatrout plot
ggplot(data = sst_mon_avg %>% filter(YEAR > 2013), mapping = aes(x = MDY, y =  CPUE_AvgSST, color = MAJOR_AREA_CODE)) + geom_line(alpha = 0.8, size = 1) + theme_classic() +#facet_wrap(~MAJOR_AREA_CODE, scale = "free") +  
  geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000")+
  geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size = 1, color = "#000000") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  labs(
    title = "Spotted Seatrout CPUE Monthly Average since 2014",
    x = "Time",
    y = "CPUE (#/hectare)"
  )+ theme(axis.text.x = element_text(angle=45, hjust=1))

#ggsave("SST_CERFTalkRedLine.jpg", width = 10, height = 8, units = c("in"), dpi = 300)


## black drum plot
ggplot(data = blackDrum_mon_avg  %>% filter(YEAR > 2013), mapping = aes(x = MDY, y =  CPUE_AvgBD, color = MAJOR_AREA_CODE)) + geom_line(alpha = 0.8, size = 1) + theme_classic() +#facet_wrap(~MAJOR_AREA_CODE, scale = "free") +  
  geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000")+
  geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size = 1, color = "#000000") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
 labs(
  title = "Black Drum CPUE Monthly Average since 2014",
  x = "Time",
  y = "CPUE (#/hectare)"
) + theme(axis.text.x = element_text(angle=45, hjust=1))

#b

#ggsave("BlackDrum_Draft.jpg", width = 10, height = 8, units = c("in"), dpi = 300)


## southern flounder plot
ggplot(data = SF_mon_avg %>% filter(YEAR > 2013), mapping = aes(x = MDY, y =  CPUE_AvgSF, color = MAJOR_AREA_CODE)) + geom_line(alpha = 0.8, size = 1) + theme_classic() + #facet_wrap(~MAJOR_AREA_CODE, scale = "free") +  
  geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000")+
  geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size = 1, color = "#000000") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  labs(
  title = "Southern Flounder CPUE Monthly Average since 2014",
  x = "Time",
  y = "CPUE (#/hectare)"
) + theme(axis.text.x = element_text(angle=45, hjust=1))

#sf

#ggsave("SF_Draft.jpg", width = 10, height = 8, units = c("in"), dpi = 300)

```

# Figure 2 
```{r ggarrange into 4 pannel figure}

rd <- ggplot(data = redDrum_mon_avg %>% filter(YEAR > 2013), mapping = aes(x = MDY, y =  CPUE_AvgRD, color = MAJOR_AREA_CODE)) + geom_line(alpha = 0.8, size = 1) +  My_Theme +
   scale_color_manual(values = colorBlindBlack8) +
geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000") + 
geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size=1, color = "#000000") +
theme_classic() + My_Theme +
   scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  labs(
  title = "Red Drum",
  x = "Time",
  color = "Bays"
) + theme(axis.text.x = element_text(angle=45, hjust=1)) 


sst <- ggplot(data = sst_mon_avg %>% filter(YEAR > 2013), mapping = aes(x = MDY, y =  CPUE_AvgSST, color = MAJOR_AREA_CODE)) + geom_line(alpha = 0.8, size = 1) + theme_classic() +
   scale_color_manual(values = colorBlindBlack8) + My_Theme +
  geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000")+
  geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size = 1, color = "#000000") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  labs(
    title = "Spotted Seatrout",
    x = "Time",
    color = "Bays"
  )+ theme(axis.text.x = element_text(angle=45, hjust=1))

bd <- ggplot(data = blackDrum_mon_avg  %>% filter(YEAR > 2013), mapping = aes(x = MDY, y =  CPUE_AvgBD, color = MAJOR_AREA_CODE)) + geom_line(alpha = 0.8, size = 1) + theme_classic() + My_Theme +
   scale_color_manual(values = colorBlindBlack8) +
  geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000")+
  geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size = 1, color = "#000000") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
 labs(
  title = "Black Drum",
  x = "Time",
  color = "Bays"
) + theme(axis.text.x = element_text(angle=45, hjust=1)) + ylim(0,350)

sf <- ggplot(data = SF_mon_avg %>% filter(YEAR > 2013), mapping = aes(x = MDY, y =  CPUE_AvgSF, color = MAJOR_AREA_CODE)) + geom_line(alpha = 0.8, size = 1) + theme_classic() + My_Theme + #facet_wrap(~MAJOR_AREA_CODE, scale = "free") +
  scale_color_manual(values = colorBlindBlack8) +
  geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000")+
  geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size = 1, color = "#000000") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  labs(
  title = "Southern Flounder",
  x = "Time",
  color = "Bays"
) + theme(axis.text.x = element_text(angle=45, hjust=1))

# arrange all 4 plots into 1 figure -----
time_series <- ggarrange(rd + rremove("ylab") + rremove("xlab"), sst +rremove("ylab") + rremove("xlab"), bd+rremove("ylab") + rremove("xlab"), sf+rremove("ylab") + rremove("xlab"), labels = NULL, common.legend = TRUE,ncol = 2, nrow = 2, legend = "top", font.label = list(size = 13, face = "bold"))

time_series

annotate_figure(time_series,
                bottom = text_grob("Time", size = 16, hjust = 1),
                left = text_grob("CPUE (#/hectare)", rot = 90, size = 16))


#annotate_figure(aransas_gn_plot, top = text_grob("Aransas Bay Gill Nets and Winter Storm Uri", color = "#8B0000", face = "bold", size = 14))

#ggsave("Figure2_edited.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")

```

# Table 1
```{r table 1 corrected, results='hide'}
#Goal: To make one table with the calculated averages and standard deviation of temperature and salinity across the bays with the numbers for the bay features that were found in the literature for each bay system.

#The laguna madre is sampled as the upper and lower laguna madre because it is so big but the bay features in the literature report it as one bay. This creates a mismatch in the number of rows at the merge.

#For the reporting of the temperature and salinity the upper and lower laguna madre will be combined for one bay sum to match the number of rows needed for the bay features table.

#Step One: Re-do the initial calculations over ten years, aggregating the averages for upper and lower into one. 

enviro_table <- bag.seines %>%
  filter(YEAR > 2013 & YEAR < 2024 ) %>% 
  group_by(MAJOR_AREA_CODE)

enviro_table <- as.data.frame(enviro_table)
#assigning the upper and the lower to both be the laguna madre to match the bay features
enviro_table$MAJOR_AREA_CODE <- sub("UpperLagunaMadre", "LagunaMadre", enviro_table$MAJOR_AREA_CODE)
enviro_table$MAJOR_AREA_CODE <- sub("LowerLagunaMadre", "LagunaMadre", enviro_table$MAJOR_AREA_CODE)

#Step Two: Conduct the summary calcualtions
#temp
enviro_tableT <- enviro_table %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarise( START_TEMPERATURE_NUM = paste(round(mean(START_TEMPERATURE_NUM), 2), round(sd(START_TEMPERATURE_NUM), 2), sep = '±')) 
#salinity
enviro_tableS <- enviro_table %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarise( START_SALINITY_NUM = paste(round(mean(START_SALINITY_NUM), 2), round(sd(START_SALINITY_NUM), 2), sep = '±')) 

#merge
enviro_join <- merge(enviro_tableT, enviro_tableS, by = "MAJOR_AREA_CODE")
enviro_join$MAJOR_AREA_CODE <- factor(enviro_join$MAJOR_AREA_CODE , levels = c("SabineLake", "GalvestonBay", "MatagordaBay", "SanAntonioBay", "AransasBay", "CorpusChristiBay", "LagunaMadre"))

#write.csv(enviro_join, "~/texas_extreme_events/enviro_join.csv", row.names=FALSE)

#Step Three: Call in environmental data from depth
table2 <- read.csv("~/texas_extreme_events/Table1_ExcelV2.csv")#from the literature
enviro_join <- read.csv("~/texas_extreme_events/enviro_join.csv") #created from original data set

#merge data
enviro_join <- enviro_join %>% 
  rename("Major.Bay" = "MAJOR_AREA_CODE") #to match table 2

table1 <- merge(table2,enviro_join, sort=FALSE)

#Step four: Rename columns
table1 <- table1 %>% 
  rename("Major Bay" = "Major.Bay") %>% 
  rename("Average Depth (m)" = "Mean.Depth..m.") %>% 
  rename("Max Depth Dredged (m)" = "Max.Depth.Dredged..m.")  %>% 
  rename("Surface Area (ha)" = "Surface.Area..ha.") %>% 
  rename("Volume (km3)" = "Volumn..km3.") %>% 
  rename("Average Temp (Celsius)" = "START_TEMPERATURE_NUM") %>% 
  rename("Average Salinity (ppt)" = "START_SALINITY_NUM")

#editing levels
table1$`Major Bay` <- factor(table1$`Major Bay` , levels = c("Sabine Lake", "Galveston Bay", "Matagorda Bay", "San Antonio Bay", "Aransas Bay", "Corpus Christi Bay", "Laguna Madre"))
levels(table1$`Major Bay`)

#Step Five: Save Table
#table_html <- kbl(table1, format = "html") %>%
#kable_styling(bootstrap_options = c("striped", "condensed"))

table1 %>% #i used this style
  kable(format = "latex", align = "lcccccc", booktabs = TRUE) %>%
  kable_classic(full_width = F, html_font = "Cambria")



```

\renewcommand{\arraystretch}{1.75}
```{r table1 print}

table1 %>% #i used this style
  kable(format = "latex", align = "lcccccc", booktabs = TRUE) %>%
  kable_classic(full_width = T, html_font = "Cambria")
```



\newpage



# Table 2

```{r Table for fish biology}
# call in data frame
FishBiology <- read.csv("~/texas_extreme_events/FishBiology.csv")

library(knitr)

FishBiology  <- FishBiology %>%
  rename("Recruitment Window" = "Recruitment.Window") %>% 
  rename("Spawning Season" = "Spawning.season")

knitr::kable(FishBiology, "pipe")

FishBiology %>% #i used this style
  kable(format = "latex", align = "llll", booktabs = TRUE) %>%
  kable_classic(full_width = T, html_font = "Cambria")

  

```


# Baseline Calculations 

In the order of Hurricane, Freeze for each 

- Red Drum
- Spotted Seatrout
- Black Drum
- Southern Flounder

# Red Drum

```{r Red Drum Hurricane}
#I had to first subset into the 10 year frame I wanted (no averaging)
check2 <- bag.seines %>%
  filter(YEAR > 2006 & YEAR < 2018 ) %>% 
  group_by(MAJOR_AREA_CODE)

#Then I had to subset for only the months I wanted for red drum (oct - end of may) given the calculations from the pulse recruitment found in the supplementals 
check3 <- check2 %>% 
  filter(MONTH < 6 ) %>% 
  group_by(MAJOR_AREA_CODE)

check4 <- check2 %>% 
  filter(MONTH > 9) %>% 
  group_by(MAJOR_AREA_CODE)
#pasting them together
finalcheck <- rbind(check3, check4)

## I realized that the data set has data from an incomplete recruitment window since it starts with 2007 in jan (this recruitment window would have started in oct of the previous year) so I need to make sure it starts in oct of 2007 and ends may of 2016 for the averages
 
finalcheck <- finalcheck %>% 
  filter(DATE > "2007-09-30") %>% 
  filter(DATE < "2017-06-01")


ggplot(finalcheck, mapping = aes(x=JULIAN_DATE, y = rd_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.RD10yr.hurricane <- finalcheck %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(rd_CPUE)) %>% 
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD10yr.hurricane$SPECIES <- "Red Drum"
RE.RD10yr.hurricane$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.RD1yr.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2017-10-01'), as.Date('2018-05-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE)) %>%
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD1yr.hurricane$SPECIES <- "Red Drum"
RE.RD1yr.hurricane$AVERAGE <- "1st year"


RE.RD2nd.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2018-10-01'), as.Date('2019-05-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE)) %>%
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD2nd.hurricane$SPECIES <- "Red Drum"
RE.RD2nd.hurricane$AVERAGE <- "2nd year"

RE.RDbyyear.Hurr <- rbind(RE.RD10yr.hurricane,RE.RD1yr.hurricane,RE.RD2nd.hurricane)


#Plotting
ggplot(data = RE.RDbyyear.Hurr , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  title = "10 yr avg vs post storm avg for RD across bays using NEW baselines",
  x = "Major bays",
  y = "Catch per Unit Effort (#/hectare)"
) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.RD.Spread.PerChange <- spread(RE.RDbyyear.Hurr, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.RD.Spread.PerChange$first_perChange <- NA
RE.RD.Spread.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.RD.Spread.PerChange)){
  RE.RD.Spread.PerChange$first_perChange[i] = format(((RE.RD.Spread.PerChange$`1st year`[i] - RE.RD.Spread.PerChange$`10 yrs`[i]) /RE.RD.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.RD.Spread.PerChange)){
  RE.RD.Spread.PerChange$second_perChange[i] = format(((RE.RD.Spread.PerChange$`2nd year`[i] - RE.RD.Spread.PerChange$`10 yrs`[i]) /RE.RD.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

## Per change values need to be converted to numeric values before plotting

RE.RD.Spread.PerChange$first_perChange <- as.numeric(RE.RD.Spread.PerChange$first_perChange)
RE.RD.Spread.PerChange$second_perChange <- as.numeric(RE.RD.Spread.PerChange$second_perChange)

##Plot
RE.RD.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange), color = '#D81B60') + geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange), color = '#1E88E5') + theme_classic() + theme(axis.text.x = element_text(angle=90, hjust=1)) + geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.02, units = "npc")),
    size = 0.3
  ) + labs(
    y = "Percent Change",
    x = "Bay Location",
    color = "legend",
    title = "Red drum during hurricane harvey with NEW baselines"
  )

  

#ggsave("RD_HHDraft.jpg", width = 10, height = 8, units = c("in"), dpi = 300)
```

```{r Red Drum Freeze}

#Red Drum
#I had to first subset into the 10 year frame I wanted (no averaging)
subset2 <- bag.seines %>%
  filter(YEAR > 2008 & YEAR < 2020 ) %>% 
  group_by(MAJOR_AREA_CODE)
#summarize(mean(rd_CPUE)) %>%
#rename("CPUE" = "mean(rd_CPUE)")

#Then I had to subset for only the months I wanted for red drum (oct - end of may)
subset3 <- subset2 %>% 
  filter(MONTH < 6 ) %>% 
  group_by(MAJOR_AREA_CODE)

subset4 <- subset2 %>% 
  filter(MONTH > 9) %>% 
  group_by(MAJOR_AREA_CODE)
#pasting them together
finalsubset <- rbind(subset3, subset4)

## I realized that the data set has data from an incomplete recruitment window since it starts with 2009 in jan (this recruitment window would have started in oct of the previous year) so I need to make sure it starts in oct of 2009 and ends may of 2019 for the averages

finalsubset <- finalsubset %>% 
  filter(DATE > "2009-09-30") %>% 
  filter(DATE < "2019-06-01")


ggplot(finalsubset, mapping = aes(x=JULIAN_DATE, y = rd_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.RD10yr.freeze <- finalsubset %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(rd_CPUE)) %>% 
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD10yr.freeze$SPECIES <- "Red Drum"
RE.RD10yr.freeze$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.RD1yr.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2021-10-01'), as.Date('2022-05-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE)) %>%
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD1yr.freeze$SPECIES <- "Red Drum"
RE.RD1yr.freeze$AVERAGE <- "1st year"


RE.RD2nd.freeze<- bag.seines %>%
  filter(between(DATE, as.Date('2022-10-01'), as.Date('2023-05-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE)) %>%
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD2nd.freeze$SPECIES <- "Red Drum"
RE.RD2nd.freeze$AVERAGE <- "2nd year"

RE.RDbyyear.Freeze <- rbind(RE.RD10yr.freeze,RE.RD1yr.freeze,RE.RD2nd.freeze)


#Plotting
ggplot(data = RE.RDbyyear.Freeze , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  title = "10 yr avg vs post freeze avg for RD across bays using NEW baselines",
  x = "Major bays",
  y = "Catch per Unit Effort (#/hectare)"
) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.RD.freeze.PerChange <- spread(RE.RDbyyear.Freeze, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.RD.freeze.PerChange$first_perChange <- NA
RE.RD.freeze.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.RD.freeze.PerChange)){
  RE.RD.freeze.PerChange$first_perChange[i] = format(((RE.RD.freeze.PerChange$`1st year`[i] - RE.RD.freeze.PerChange$`10 yrs`[i]) /RE.RD.freeze.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.RD.freeze.PerChange)){
  RE.RD.freeze.PerChange$second_perChange[i] = format(((RE.RD.freeze.PerChange$`2nd year`[i] - RE.RD.freeze.PerChange$`10 yrs`[i]) /RE.RD.freeze.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

## Per change values need to be converted to numeric values before plotting
RE.RD.freeze.PerChange$first_perChange <- as.numeric(RE.RD.freeze.PerChange$first_perChange)
RE.RD.freeze.PerChange$second_perChange <- as.numeric(RE.RD.freeze.PerChange$second_perChange)

##Plot
RE.RD.freeze.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange), color = '#D81B60') + geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange), color = '#1E88E5') + theme_classic() + theme(axis.text.x = element_text(angle=90, hjust=1)) + geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.02, units = "npc")),
    size = 0.3
  ) + labs(
    y = "Percent Change",
    x = "Bay Location",
    color = "legend",
    title = "Red drum during freeze with NEW baselines"
  )

#ggsave("RD_FreezeDraft.jpg", width = 10, height = 8, units = c("in"), dpi = 300)
```




# Spotted Seatrout

```{r Spotted Seatrout Hurricane }

#I had to first subset into the 10 year frame I wanted (no averaging)
subset5 <- bag.seines %>%
  filter(YEAR > 2006 & YEAR < 2017 ) %>% 
  group_by(MAJOR_AREA_CODE)

#Then I had to subset for only the months I wanted for spotted seatrout (june - end of december)
subset6 <- subset5 %>% 
  filter(MONTH > 5 ) %>% 
  group_by(MAJOR_AREA_CODE)

ggplot(subset6, mapping = aes(x=JULIAN_DATE, y = sst_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.SST10yr.hurricane <- subset6 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(sst_CPUE)) %>% 
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST10yr.hurricane$SPECIES <- "Spotted Seatrout"
RE.SST10yr.hurricane$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.SST1yr.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2018-06-01'), as.Date('2018-12-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE)) %>%
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST1yr.hurricane$SPECIES <- "Spotted Seatrout"
RE.SST1yr.hurricane$AVERAGE <- "1st year"


RE.SST2nd.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2019-06-01'), as.Date('2019-12-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE)) %>%
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST2nd.hurricane$SPECIES <- "Spotted Seatrout"
RE.SST2nd.hurricane$AVERAGE <- "2nd year"

RE.SSTbyyear.Hurr <- rbind(RE.SST10yr.hurricane,RE.SST1yr.hurricane,RE.SST2nd.hurricane)


#Plotting
ggplot(data = RE.SSTbyyear.Hurr , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  title = "10 yr avg vs post storm avg for SST across bays using NEW baselines",
  x = "Major bays",
  y = "Catch per Unit Effort (#/hectare)"
) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

## PERCENT CHANGES
#make it wide:
RE.SST.Spread.PerChange <- spread(RE.SSTbyyear.Hurr, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.SST.Spread.PerChange$first_perChange <- NA
RE.SST.Spread.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.SST.Spread.PerChange)){
  RE.SST.Spread.PerChange$first_perChange[i] = format(((RE.SST.Spread.PerChange$`1st year`[i] - RE.SST.Spread.PerChange$`10 yrs`[i]) /RE.SST.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.SST.Spread.PerChange)){
  RE.SST.Spread.PerChange$second_perChange[i] = format(((RE.SST.Spread.PerChange$`2nd year`[i] - RE.SST.Spread.PerChange$`10 yrs`[i]) /RE.SST.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

## Per change values need to be converted to numeric values before plotting

RE.SST.Spread.PerChange$first_perChange <- as.numeric(RE.SST.Spread.PerChange$first_perChange)
RE.SST.Spread.PerChange$second_perChange <- as.numeric(RE.SST.Spread.PerChange$second_perChange)

##Plot
My_Theme <- theme(
  axis.title.x = element_text(size = 12),
  axis.text.x = element_text(size = 12),
  axis.title.y = element_text(size = 12),
  plot.title = element_text(size = 12),
  legend.text = element_text(size = 12),
  legend.title = element_text(size = 12),
  axis.ticks.length = unit(0.20, "cm"),
  axis.text.y = element_text(size = 12))


RE.SST.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) + geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm"
  )



#ggsave("SST_HHPerChangeCERF.jpg", width = 10, height = 8, units = c("in"), dpi = 300)



```

```{r Spotted Seatrout Freeze}
# Spotted seatrout freeze baseline
#I had to first subset into the 10 year frame I wanted (no averaging)
subset7 <- bag.seines %>%
  filter(YEAR > 2009 & YEAR < 2020 ) %>% 
  group_by(MAJOR_AREA_CODE)
#summarize(mean(rd_CPUE)) %>%
#rename("CPUE" = "mean(rd_CPUE)")

#Then I had to subset for only the months I wanted for spotted seatrout (june - end of dec)
subset8 <- subset7 %>% 
  filter(MONTH > 5 ) %>% 
  group_by(MAJOR_AREA_CODE)

ggplot(subset8, mapping = aes(x=JULIAN_DATE, y = sst_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.SST10yr.freeze <- subset8 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(sst_CPUE)) %>% 
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST10yr.freeze$SPECIES <- "Spotted Seatrout"
RE.SST10yr.freeze$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.SST1yr.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2021-06-01'), as.Date('2021-12-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE)) %>%
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST1yr.freeze$SPECIES <- "Spotted Seatrout"
RE.SST1yr.freeze$AVERAGE <- "1st year"


RE.SST2nd.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2022-06-01'), as.Date('2022-12-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE)) %>%
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST2nd.freeze$SPECIES <- "Spotted Seatrout"
RE.SST2nd.freeze$AVERAGE <- "2nd year"

RE.SSTbyyear.Freeze <- rbind(RE.SST10yr.freeze,RE.SST1yr.freeze,RE.SST2nd.freeze)


#Plotting
ggplot(data = RE.SSTbyyear.Freeze , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  title = "10 yr avg vs post storm avg for SST across bays using NEW baselines",
  x = "Major bays",
  y = "Catch per Unit Effort (#/hectare)"
) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.SST.PerChange.freeze <- spread(RE.SSTbyyear.Freeze, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.SST.PerChange.freeze$first_perChange <- NA
RE.SST.PerChange.freeze$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.SST.PerChange.freeze)){
  RE.SST.PerChange.freeze$first_perChange[i] = format(((RE.SST.PerChange.freeze$`1st year`[i] - RE.SST.PerChange.freeze$`10 yrs`[i]) /RE.SST.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.SST.PerChange.freeze)){
  RE.SST.PerChange.freeze$second_perChange[i] = format(((RE.SST.PerChange.freeze$`2nd year`[i] - RE.SST.PerChange.freeze$`10 yrs`[i]) /RE.SST.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

## Per change values need to be converted to numeric values before plotting

RE.SST.PerChange.freeze$first_perChange <- as.numeric(RE.SST.PerChange.freeze$first_perChange)
RE.SST.PerChange.freeze$second_perChange <- as.numeric(RE.SST.PerChange.freeze$second_perChange)

##Plot
RE.SST.PerChange.freeze %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) + geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + theme_classic() +theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) +#ylim(-60,60) +
  labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm"
  ) 



#ggsave("SST_CERFFreezeZoom.jpg", width = 10, height = 8, units = c("in"), dpi = 300)

```



# Black Drum 

```{r Black drum Hurricane}
## Recruitment window is April to end of oct 
#I had to first subset into the 10 year frame I wanted (no averaging)
subset9 <- bag.seines %>%
  filter(YEAR > 2006 & YEAR < 2017 ) %>% 
  group_by(MAJOR_AREA_CODE)


#Then I had to subset for only the months I wanted for black drum (April to end of oct)
subset10 <- subset9 %>% 
  filter(MONTH > 3 & MONTH < 11 ) %>% 
  group_by(MAJOR_AREA_CODE)

ggplot(subset10, mapping = aes(x=JULIAN_DATE, y = bd_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.BD10yr.hurricane <- subset10 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(bd_CPUE)) %>% 
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD10yr.hurricane$SPECIES <- "Black Drum"
RE.BD10yr.hurricane$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.BD1yr.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2018-04-01'), as.Date('2018-10-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE)) %>%
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD1yr.hurricane$SPECIES <- "Black Drum"
RE.BD1yr.hurricane$AVERAGE <- "1st year"


RE.BD2nd.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2019-04-01'), as.Date('2019-10-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE)) %>%
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD2nd.hurricane$SPECIES <- "Black Drum"
RE.BD2nd.hurricane$AVERAGE <- "2nd year"

RE.BDbyyear.Hurr <- rbind(RE.BD10yr.hurricane,RE.BD1yr.hurricane,RE.BD2nd.hurricane)


#Plotting
ggplot(data = RE.BDbyyear.Hurr , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  title = "10 yr avg vs post storm avg for BD across bays using NEW baselines",
  x = "Major bays",
  y = "Catch per Unit Effort (#/hectare)"
) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

## PERCENT CHANGES
#make it wide:
RE.BD.Spread.PerChange <- spread(RE.BDbyyear.Hurr, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.BD.Spread.PerChange$first_perChange <- NA
RE.BD.Spread.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.BD.Spread.PerChange)){
  RE.BD.Spread.PerChange$first_perChange[i] = format(((RE.BD.Spread.PerChange$`1st year`[i] - RE.BD.Spread.PerChange$`10 yrs`[i]) /RE.BD.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.BD.Spread.PerChange)){
  RE.BD.Spread.PerChange$second_perChange[i] = format(((RE.BD.Spread.PerChange$`2nd year`[i] - RE.BD.Spread.PerChange$`10 yrs`[i]) /RE.BD.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

## Per change values need to be converted to numeric values before plotting

RE.BD.Spread.PerChange$first_perChange <- as.numeric(RE.BD.Spread.PerChange$first_perChange)

RE.BD.Spread.PerChange$second_perChange <- as.numeric(RE.BD.Spread.PerChange$second_perChange)

##Plot
RE.BD.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange), color = '#D81B60') + geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange), color = '#1E88E5') + theme_classic() + theme(axis.text.x = element_text(angle=90, hjust=1)) + geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.02, units = "npc")),
    size = 0.3
  ) + labs(
    y = "Percent Change",
    x = "Bay Location",
    color = "legend",
    title = "BD during hurricane harvey with NEW baselines"
  )

#ggsave("BD_HHPerChangeDraft.jpg", width = 10, height = 8, units = c("in"), dpi = 300)

```


```{r Black Drum Freeze}

# black drum freeze baseline
#I had to first subset into the 10 year frame I wanted (no averaging)
subset11 <- bag.seines %>%
  filter(YEAR > 2009 & YEAR < 2020 ) %>% 
  group_by(MAJOR_AREA_CODE)

#Then I had to subset for only the months I wanted for black drum (April - end of oct)
subset12 <- subset11 %>% 
  filter(MONTH > 3 & MONTH < 11 ) %>% 
  group_by(MAJOR_AREA_CODE)

ggplot(subset12, mapping = aes(x=JULIAN_DATE, y = bd_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.BD10yr.freeze <- subset12 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(bd_CPUE)) %>% 
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD10yr.freeze$SPECIES <- "Black Drum"
RE.BD10yr.freeze$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.BD1yr.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2021-04-01'), as.Date('2021-10-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE)) %>%
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD1yr.freeze$SPECIES <- "Black Drum"
RE.BD1yr.freeze$AVERAGE <- "1st year"


RE.BD2nd.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2022-04-01'), as.Date('2022-10-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE)) %>%
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD2nd.freeze$SPECIES <- "Black Drum"
RE.BD2nd.freeze$AVERAGE <- "2nd year"

RE.BDbyyear.Freeze <- rbind(RE.BD10yr.freeze,RE.BD1yr.freeze,RE.BD2nd.freeze)


#Plotting
ggplot(data = RE.BDbyyear.Freeze , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  title = "10 yr avg vs post storm avg for BD across bays using NEW baselines",
  x = "Major bays",
  y = "Catch per Unit Effort (#/hectare)"
) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.BD.PerChange.freeze <- spread(RE.BDbyyear.Freeze, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.BD.PerChange.freeze$first_perChange <- NA
RE.BD.PerChange.freeze$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.BD.PerChange.freeze)){
  RE.BD.PerChange.freeze$first_perChange[i] = format(((RE.BD.PerChange.freeze$`1st year`[i] - RE.BD.PerChange.freeze$`10 yrs`[i]) /RE.BD.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.BD.PerChange.freeze)){
  RE.BD.PerChange.freeze$second_perChange[i] = format(((RE.BD.PerChange.freeze$`2nd year`[i] - RE.BD.PerChange.freeze$`10 yrs`[i]) /RE.BD.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

## Per change values need to be converted to numeric values before plotting

RE.BD.PerChange.freeze$first_perChange <- as.numeric(RE.BD.PerChange.freeze$first_perChange)
RE.BD.PerChange.freeze$second_perChange <- as.numeric(RE.BD.PerChange.freeze$second_perChange)

##Plot


RE.BD.PerChange.freeze %>%
    ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) + geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + theme_classic() +theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 15 )  +
  labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm"
  ) 


#ggsave("BD_CERFFreeze.jpg", width = 10, height = 8, units = c("in"), dpi = 300)

```



# Southern Flounder

```{r Souther Flounder Hurricane}

## Recruitment window is feb to end of july

#I had to first subset into the 10 year frame I wanted (no averaging)
subset13 <- bag.seines %>%
  filter(YEAR > 2006 & YEAR < 2017 ) %>% 
  group_by(MAJOR_AREA_CODE)


#Then I had to subset for only the months I wanted for southern flounder (feb - end of july)
subset14 <- subset13 %>% 
  filter(MONTH > 1 & MONTH < 8 ) %>% 
  group_by(MAJOR_AREA_CODE)

ggplot(subset14, mapping = aes(x=JULIAN_DATE, y = sf_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.SF10yr.hurricane <- subset14 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(sf_CPUE)) %>% 
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF10yr.hurricane$SPECIES <- "Southern Flounder"
RE.SF10yr.hurricane$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.SF1yr.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2018-02-01'), as.Date('2018-07-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE)) %>%
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF1yr.hurricane$SPECIES <- "Southern Flounder"
RE.SF1yr.hurricane$AVERAGE <- "1st year"


RE.SF2nd.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2019-02-01'), as.Date('2019-07-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE)) %>%
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF2nd.hurricane$SPECIES <- "Southern Flounder"
RE.SF2nd.hurricane$AVERAGE <- "2nd year"

RE.SFbyyear.Hurr <- rbind(RE.SF10yr.hurricane,RE.SF1yr.hurricane,RE.SF2nd.hurricane)


#Plotting
ggplot(data = RE.SFbyyear.Hurr , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  title = "10 yr avg vs post storm avg for SF across bays using NEW baselines",
  x = "Major bays",
  y = "Catch per Unit Effort (#/hectare)"
) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

## PERCENT CHANGES
#make it wide:
RE.SF.Spread.PerChange <- spread(RE.SFbyyear.Hurr, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.SF.Spread.PerChange$first_perChange <- NA
RE.SF.Spread.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.SF.Spread.PerChange)){
  RE.SF.Spread.PerChange$first_perChange[i] = format(((RE.SF.Spread.PerChange$`1st year`[i] - RE.SF.Spread.PerChange$`10 yrs`[i]) /RE.SF.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.SF.Spread.PerChange)){
  RE.SF.Spread.PerChange$second_perChange[i] = format(((RE.SF.Spread.PerChange$`2nd year`[i] - RE.SF.Spread.PerChange$`10 yrs`[i]) /RE.SF.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

## Per change values need to be converted to numeric values before plotting

RE.SF.Spread.PerChange$first_perChange <- as.numeric(RE.SF.Spread.PerChange$first_perChange)
RE.SF.Spread.PerChange$second_perChange <- as.numeric(RE.SF.Spread.PerChange$second_perChange)

##Plot
RE.SF.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange), color = '#D81B60') + geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange), color = '#1E88E5') + theme_classic() + theme(axis.text.x = element_text(angle=90, hjust=1)) + geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.02, units = "npc")),
    size = 0.3
  ) + labs(
    y = "Percent Change",
    x = "Bay Location",
    color = "legend",
    title = "SF during hurricane harvey with NEW baselines"
  )


#ggsave("SF_HHPerChangeDraft.jpg", width = 10, height = 8, units = c("in"), dpi = 300)




```

```{r Southern Flounder Freeze}
# southern flounder freeze baseline
#I had to first subset into the 10 year frame I wanted (no averaging)
subset15 <- bag.seines %>%
  filter(YEAR > 2009 & YEAR < 2020 ) %>% 
  group_by(MAJOR_AREA_CODE)

#Then I had to subset for only the months I wanted for southern flounder feb -end of july
subset16 <- subset15 %>% 
  filter(MONTH > 1 & MONTH < 8 ) %>% 
  group_by(MAJOR_AREA_CODE)

ggplot(subset16, mapping = aes(x=JULIAN_DATE, y = sf_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.SF10yr.freeze <- subset16 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(sf_CPUE)) %>% 
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF10yr.freeze$SPECIES <- "Southern Flounder"
RE.SF10yr.freeze$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.SF1yr.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2021-02-22'), as.Date('2021-07-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE)) %>%
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF1yr.freeze$SPECIES <- "Southern Flounder"
RE.SF1yr.freeze$AVERAGE <- "1st year"


RE.SF2nd.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2022-02-22'), as.Date('2022-07-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE)) %>%
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF2nd.freeze$SPECIES <- "Southern Flounder"
RE.SF2nd.freeze$AVERAGE <- "2nd year"

RE.SFbyyear.Freeze <- rbind(RE.SF10yr.freeze,RE.SF1yr.freeze,RE.SF2nd.freeze)


#Plotting
ggplot(data = RE.SFbyyear.Freeze , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  title = "10 yr avg vs post storm avg for SF across bays using NEW baselines",
  x = "Major bays",
  y = "Catch per Unit Effort (#/hectare)"
) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.SF.PerChange.freeze <- spread(RE.SFbyyear.Freeze, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.SF.PerChange.freeze$first_perChange <- NA
RE.SF.PerChange.freeze$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.SF.PerChange.freeze)){
  RE.SF.PerChange.freeze$first_perChange[i] = format(((RE.SF.PerChange.freeze$`1st year`[i] - RE.SF.PerChange.freeze$`10 yrs`[i]) /RE.SF.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.SF.PerChange.freeze)){
  RE.SF.PerChange.freeze$second_perChange[i] = format(((RE.SF.PerChange.freeze$`2nd year`[i] - RE.SF.PerChange.freeze$`10 yrs`[i]) /RE.SF.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

## Per change values need to be converted to numeric values before plotting

RE.SF.PerChange.freeze$first_perChange <- as.numeric(RE.SF.PerChange.freeze$first_perChange)
RE.SF.PerChange.freeze$second_perChange <- as.numeric(RE.SF.PerChange.freeze$second_perChange)

##Plot
RE.SF.PerChange.freeze %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange), color = '#D81B60') + geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange), color = '#1E88E5') + theme_classic() + theme(axis.text.x = element_text(angle=90, hjust=1)) + geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.02, units = "npc")),
    size = 0.3
  ) + labs(
    y = "Percent Change",
    x = "Bay Location",
    color = "legend",
    title = "SF during freeze with NEW baselines"
  )

#ggsave("SF_FreezeDraft.jpg", width = 10, height = 8, units = c("in"), dpi = 300)

```


# Accounting for annual variaiton Analysis 
## Here we calculate the year to year percent change in the 10 year baseline period. From these numbers we created boxplots and then put thme on top of the percent change figures to give a range of expected interanual variablity. 

This is organized by species:
- Spotted seatrout and Hurricane
- Spotted seatrout and Freeze 
- Black Drum and Hurricane
- Black Drum and Freeze
- SF and Hurricane
- SF and Freeze
- RD and Freeze
- RD and Hurricane


# Spotted seatrout Added Boxplot
```{r Spotted Seatrout and Hurricane }
# Testing percent change averages
sp.hur <- subset6 %>% 
  group_by(MAJOR_AREA_CODE,YEAR) %>% 
  summarize(mean(sst_CPUE)) %>% 
  rename("CPUE" = "mean(sst_CPUE)")

sp.hur$SPECIES <- "Spotted Seatrout"

sp.hur$MAJOR_AREA_CODE <- as.character(sp.hur$MAJOR_AREA_CODE)

#nested for loop for the calculations
bayTitle <- unique(sp.hur$MAJOR_AREA_CODE)
yearly_change <-  data.frame(matrix(ncol = 3, nrow = 0))
colnames(yearly_change) <- c('Bays', 'Year', 'per_change')

for (i in 1:length(bayTitle)){
  newdataCheck <- sp.hur %>% 
    filter(MAJOR_AREA_CODE == bayTitle[i]) %>% 
    arrange(YEAR)
  for (j in 1:(nrow(newdataCheck)-1)) {
    changeCheck <- format(((newdataCheck$CPUE[j+1]-newdataCheck$CPUE[j])/newdataCheck$CPUE[j]) * 100, scientific = F)
    newrows <- data.frame(Bays = bayTitle[i], Year = newdataCheck$YEAR[j+1], per_change =changeCheck)
    yearly_change <- rbind(yearly_change, newrows)
  }
}




#done

#boxplot making
library(tidyverse)
library("hrbrthemes")
library(viridis)

yearly_change$Bays <- as.factor(yearly_change$Bays)
library(forcats)
levels(yearly_change$Bays)
yearly_change$Bays <- fct_inorder(yearly_change$Bays)
yearly_change$per_change <- as.numeric(yearly_change$per_change)


yearly_change %>%
  ggplot( aes(x=Bays, y=per_change, fill=Bays)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=1, alpha=0.6) +
    theme_ipsum() + theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle=45, hjust=1)
    ) 


### Adding it to the percent change plot
RE.SST.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + 
  geom_boxplot(data = yearly_change, aes(x=Bays, y=per_change, fill=Bays), coef=0, outlier.shape = NA) +
   scale_fill_viridis(discrete = TRUE, alpha=0.2) +
    theme_ipsum()+
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "spotted seatrout and HH"
  )

#ggsave("test1_SSTBoxplots.jpg", width = 10, height = 8, units = c("in"), dpi = 300)


```


```{r Spotted seatrout and Freeze}
# Testing percent change averages
sp.freeze <- subset8 %>% 
  group_by(MAJOR_AREA_CODE,YEAR) %>% 
  summarize(mean(sst_CPUE)) %>% 
  rename("CPUE" = "mean(sst_CPUE)")

sp.freeze$SPECIES <- "Spotted Seatrout"

sp.freeze$MAJOR_AREA_CODE <- as.character(sp.freeze$MAJOR_AREA_CODE)

#nested for loop for the calculations
sp.bayTitle <- unique(sp.freeze$MAJOR_AREA_CODE)
sp.yearly_change <-  data.frame(matrix(ncol = 3, nrow = 0))
colnames(sp.yearly_change) <- c('Bays', 'Year', 'per_change')

for (i in 1:length(sp.bayTitle)){
  new.sp <- sp.freeze %>% 
    filter(MAJOR_AREA_CODE == sp.bayTitle[i]) %>% 
    arrange(YEAR)
  for (j in 1:(nrow(new.sp)-1)) {
    change.sp <- format(((new.sp$CPUE[j+1]-new.sp$CPUE[j])/new.sp$CPUE[j]) * 100, scientific = F)
    newrow.sp <- data.frame(Bays = sp.bayTitle[i], Year = new.sp$YEAR[j+1], per_change =change.sp)
    sp.yearly_change <- rbind(sp.yearly_change, newrow.sp)
  }
}

#done

#boxplot making
library(tidyverse)
library("hrbrthemes")
library(viridis)
library(forcats)

#re-ordering the levels
sp.yearly_change$Bays <- as.factor(sp.yearly_change$Bays)

levels(sp.yearly_change$Bays)
sp.yearly_change$Bays <- fct_inorder(sp.yearly_change$Bays)
sp.yearly_change$per_change <- as.numeric(sp.yearly_change$per_change)


sp.yearly_change %>%
  ggplot( aes(x=Bays, y=per_change, fill=Bays)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=1, alpha=0.6) +
    theme_ipsum() + theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle=45, hjust=1)
    ) 

### Adding it to the percent change plot
RE.SST.PerChange.freeze %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + 
  geom_boxplot(data = sp.yearly_change, aes(x=Bays, y=per_change, fill=Bays), coef=0, outlier.shape = NA) +
   scale_fill_viridis(discrete = TRUE, alpha=0.2) +
    theme_ipsum()+
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "spotted seatrout and Freeze"
  )
```

#Black drum added boxplot

```{r Black Drum and Hurricane Harvey}
# Testing percent change averages
bd.hur <- subset10 %>% 
  group_by(MAJOR_AREA_CODE,YEAR) %>% 
  summarize(mean(bd_CPUE)) %>% 
  rename("CPUE" = "mean(bd_CPUE)")

bd.hur$SPECIES <- "Black Drum"

bd.hur$MAJOR_AREA_CODE <- as.character(bd.hur$MAJOR_AREA_CODE)

#nested for loop for the calculations
bdHH.bayTitle <- unique(bd.hur$MAJOR_AREA_CODE)
bdHH.yearly_change <-  data.frame(matrix(ncol = 3, nrow = 0))
colnames(bdHH.yearly_change) <- c('Bays', 'Year', 'per_change')

for (i in 1:length(bdHH.bayTitle)){
  new.bdHH <- bd.hur %>% 
    filter(MAJOR_AREA_CODE == bdHH.bayTitle[i]) %>% 
    arrange(YEAR)
  for (j in 1:(nrow(new.bdHH)-1)) {
    change.bdHH <- format(((new.bdHH$CPUE[j+1]-new.bdHH$CPUE[j])/new.bdHH$CPUE[j]) * 100, scientific = F)
    newrow.bdHH <- data.frame(Bays = bdHH.bayTitle[i], Year = new.bdHH$YEAR[j+1], per_change =change.bdHH)
    bdHH.yearly_change <- rbind(bdHH.yearly_change, newrow.bdHH)
  }
}



#done

#boxplot making
library(tidyverse)
library("hrbrthemes")
library(viridis)
library(forcats)

#re-ordering the levels
bdHH.yearly_change$Bays <- as.factor(bdHH.yearly_change$Bays)

levels(bdHH.yearly_change$Bays)
bdHH.yearly_change$Bays <- fct_inorder(bdHH.yearly_change$Bays)
bdHH.yearly_change$per_change <- as.numeric(bdHH.yearly_change$per_change)


bdHH.yearly_change %>%
  ggplot( aes(x=Bays, y=per_change, fill=Bays)) +
    geom_boxplot(outlier.shape = NA, coef=0) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6)  +
    theme_ipsum() + theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle=45, hjust=1)
    ) 

#convert inf values to true 0's
bdHH.yearly_change <- bdHH.yearly_change %>%
  mutate(across(where(is.numeric), ~ ifelse(is.infinite(.), 0, .)))

### Adding it to the percent change plot
RE.BD.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + 
  geom_boxplot(data = bdHH.yearly_change, aes(x=Bays, y=per_change, fill=Bays), coef=0, outlier.shape = NA) +
   scale_fill_viridis(discrete = TRUE, alpha=0.2) +
    theme_ipsum()+
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "black drum and hurricane harvey"
  ) +coord_cartesian(ylim = c(-100,500))




```

```{r Black Drum and Freeze}
# Testing percent change averages
bd.freeze <- subset12 %>% 
  group_by(MAJOR_AREA_CODE,YEAR) %>% 
  summarize(mean(bd_CPUE)) %>% 
  rename("CPUE" = "mean(bd_CPUE)")

bd.freeze$SPECIES <- "Black Drum"

bd.freeze$MAJOR_AREA_CODE <- as.character(bd.freeze$MAJOR_AREA_CODE)

#nested for loop for the calculations
bd.bayTitle <- unique(bd.freeze$MAJOR_AREA_CODE)
bd.yearly_change <-  data.frame(matrix(ncol = 3, nrow = 0))
colnames(bd.yearly_change) <- c('Bays', 'Year', 'per_change')

for (i in 1:length(bd.bayTitle)){
  new.bd <- bd.freeze %>% 
    filter(MAJOR_AREA_CODE == bd.bayTitle[i]) %>% 
    arrange(YEAR)
  for (j in 1:(nrow(new.bd)-1)) {
    change.bd <- format(((new.bd$CPUE[j+1]-new.bd$CPUE[j])/new.bd$CPUE[j]) * 100, scientific = F)
    newrow.bd <- data.frame(Bays = bd.bayTitle[i], Year = new.bd$YEAR[j+1], per_change =change.bd)
    bd.yearly_change <- rbind(bd.yearly_change, newrow.bd)
  }
}



#done

#boxplot making
library(tidyverse)
library("hrbrthemes")
library(viridis)
library(forcats)

#re-ordering the levels
bd.yearly_change$Bays <- as.factor(bd.yearly_change$Bays)

levels(bd.yearly_change$Bays)
bd.yearly_change$Bays <- fct_inorder(bd.yearly_change$Bays)
bd.yearly_change$per_change <- as.numeric(bd.yearly_change$per_change)


bd.yearly_change %>%
  ggplot( aes(x=Bays, y=per_change, fill=Bays)) +
    geom_boxplot(outlier.shape = NA, coef=0) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6)  +
    theme_ipsum() + theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle=45, hjust=1)
    ) 

#convert inf values to true 0's
bd.yearly_change <- bd.yearly_change %>%
  mutate(across(where(is.numeric), ~ ifelse(is.infinite(.), 0, .)))

### Adding it to the percent change plot
RE.BD.PerChange.freeze %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + 
  geom_boxplot(data = bd.yearly_change, aes(x=Bays, y=per_change, fill=Bays), coef=0, outlier.shape = NA) +
   scale_fill_viridis(discrete = TRUE, alpha=0.2) +
    theme_ipsum()+
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "black drum and freeze"
  ) 


```


# Southern Flounder added box plots

```{r Southern Flounder and Hurricanes}
# Testing percent change averages 
sf.hur <- subset14 %>% 
  group_by(MAJOR_AREA_CODE,YEAR) %>% 
  summarize(mean(sf_CPUE)) %>% 
  rename("CPUE" = "mean(sf_CPUE)")

sf.hur$SPECIES <- "Southern flounder"

sf.hur$MAJOR_AREA_CODE <- as.character(sf.hur$MAJOR_AREA_CODE)

#nested for loop for the calculations
sfHH.bayTitle <- unique(sf.hur$MAJOR_AREA_CODE)
sfHH.yearly_change <-  data.frame(matrix(ncol = 3, nrow = 0))
colnames(sfHH.yearly_change) <- c('Bays', 'Year', 'per_change')

for (i in 1:length(sfHH.bayTitle)){
  new.sfHH <- sf.hur %>% 
    filter(MAJOR_AREA_CODE == sfHH.bayTitle[i]) %>% 
    arrange(YEAR)
  for (j in 1:(nrow(new.sfHH)-1)) {
    change.sfHH <- format(((new.sfHH$CPUE[j+1]-new.sfHH$CPUE[j])/new.sfHH$CPUE[j]) * 100, scientific = F)
    newrow.sfHH <- data.frame(Bays = sfHH.bayTitle[i], Year = new.sfHH$YEAR[j+1], per_change =change.sfHH)
    sfHH.yearly_change <- rbind(sfHH.yearly_change, newrow.sfHH)
  }
}




#done


#re-ordering the levels
sfHH.yearly_change$Bays <- as.factor(sfHH.yearly_change$Bays)

levels(sfHH.yearly_change$Bays)
sfHH.yearly_change$Bays <- fct_inorder(sfHH.yearly_change$Bays)
sfHH.yearly_change$per_change <- as.numeric(sfHH.yearly_change$per_change)


sfHH.yearly_change %>%
  ggplot( aes(x=Bays, y=per_change, fill=Bays)) +
    geom_boxplot(outlier.shape = NA, coef=0) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6)  +
    theme_ipsum() + theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle=45, hjust=1)
    ) +coord_cartesian(ylim = c(-120,500))

#convert inf values to true 0's
sfHH.yearly_change <- sfHH.yearly_change %>%
  mutate(across(where(is.numeric), ~ ifelse(is.infinite(.), 0, .)))

### Adding it to the percent change plot
RE.SF.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + 
  geom_boxplot(data = sfHH.yearly_change, aes(x=Bays, y=per_change, fill=Bays), coef=0, outlier.shape = NA) +
   scale_fill_viridis(discrete = TRUE, alpha=0.2) +
    theme_ipsum()+
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "southern flounder and hurricane harvey"
  ) +coord_cartesian(ylim = c(-120,500))


```

```{r southern flounder and freeze}
# Testing percent change averages
sf.freeze <- subset16 %>% 
  group_by(MAJOR_AREA_CODE,YEAR) %>% 
  summarize(mean(sf_CPUE)) %>% 
  rename("CPUE" = "mean(sf_CPUE)")

sf.freeze$SPECIES <- "Southern flounder"

sf.freeze$MAJOR_AREA_CODE <- as.character(sf.freeze$MAJOR_AREA_CODE)

#nested for loop for the calculations
sf.bayTitle <- unique(sf.freeze$MAJOR_AREA_CODE)
sf.yearly_change <-  data.frame(matrix(ncol = 3, nrow = 0))
colnames(sf.yearly_change) <- c('Bays', 'Year', 'per_change')

for (i in 1:length(sf.bayTitle)){
  new.sf <- sf.freeze %>% 
    filter(MAJOR_AREA_CODE == sf.bayTitle[i]) %>% 
    arrange(YEAR)
  for (j in 1:(nrow(new.sf)-1)) {
    change.sf <- format(((new.sf$CPUE[j+1]-new.sf$CPUE[j])/new.sf$CPUE[j]) * 100, scientific = F)
    newrow.sf <- data.frame(Bays = sf.bayTitle[i], Year = new.sf$YEAR[j+1], per_change =change.sf)
    sf.yearly_change <- rbind(sf.yearly_change, newrow.sf)
  }
}


#done

#boxplot making


#re-ordering the levels
sf.yearly_change$Bays <- as.factor(sf.yearly_change$Bays)

levels(sf.yearly_change$Bays)
sf.yearly_change$Bays <- fct_inorder(sf.yearly_change$Bays)
sf.yearly_change$per_change <- as.numeric(sf.yearly_change$per_change)


sf.yearly_change %>%
  ggplot( aes(x=Bays, y=per_change, fill=Bays)) +
    geom_boxplot(outlier.shape = NA, coef=0) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6)  +
    theme_ipsum() + theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle=45, hjust=1)
    ) + ylim(-120,200)

#convert inf values to true 0's
sf.yearly_change <- sf.yearly_change %>%
  mutate(across(where(is.numeric), ~ ifelse(is.infinite(.), 0, .)))


### Adding it to the percent change plot
RE.SF.PerChange.freeze %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + 
  geom_boxplot(data = sf.yearly_change, aes(x=Bays, y=per_change, fill=Bays), coef=0, outlier.shape = NA) +
   scale_fill_viridis(discrete = TRUE, alpha=0.2) +
    theme_ipsum()+
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "southern flounder and freeze"
  ) +coord_cartesian(ylim = c(-120,1000))

```

# Red Drum added boxplots

```{r Red Drum and freeze}

## Setting up the data frame, a function and a for loop needed to be made
rd.freeze <- finalsubset
rd.freeze <- add_column(rd.freeze, RecruitmentYear = NA)

freeze_function <- function(DATE){
  if (DATE > "2009-09-30" & DATE < "2010-06-01"){
    (RecruitmentYear = 'Year 1')
  }else if(DATE > "2010-09-30" & DATE < "2011-06-01"){
    (RecruitmentYear = 'Year 2')
  }else if (DATE > "2011-09-30" & DATE < "2012-06-01"){
    (RecruitmentYear = 'Year 3')
  }else if (DATE > "2012-09-30" & DATE < "2013-06-01"){
    (RecruitmentYear = 'Year 4')
  }else if (DATE > "2013-09-30" & DATE < "2014-06-01"){
    (RecruitmentYear = 'Year 5')
  }else if (DATE > "2014-09-30" & DATE < "2015-06-01"){
    (RecruitmentYear = 'Year 6')
  }else if (DATE > "2015-09-30" & DATE < "2016-06-01"){
    (RecruitmentYear = 'Year 7')
  }else if (DATE > "2016-09-30" & DATE < "2017-06-01"){
    (RecruitmentYear = 'Year 8')
  }else if (DATE > "2017-09-30" & DATE < "2018-06-01"){
    (RecruitmentYear = 'Year 9')
  }else(RecruitmentYear = 'Year 10')
  return(RecruitmentYear)
}

for (i in 1:nrow(rd.freeze)){
  DATE <- rd.freeze[i, "DATE"]
  rd.freeze[i,"RecruitmentYear"] <- freeze_function(DATE)
}

### Now it can start like the rest of the r chunks
rd.freeze2 <- rd.freeze %>% 
  group_by(MAJOR_AREA_CODE,RecruitmentYear) %>% 
  summarize(mean(rd_CPUE)) %>% 
  rename("CPUE" = "mean(rd_CPUE)")

rd.freeze2$SPECIES <- "Red Drum"

# Re-ordering the years in the factors
rd.freeze2$MAJOR_AREA_CODE <- as.character(rd.freeze2$MAJOR_AREA_CODE)
rd.freeze2$RecruitmentYear <- as.factor(rd.freeze2$RecruitmentYear)
rd.freeze2$RecruitmentYear <- factor(rd.freeze2$RecruitmentYear, levels = c("Year 1", "Year 2", "Year 3", "Year 4", "Year 5", "Year 6", "Year 7", "Year 8", "Year 9", "Year 10"))

levels(rd.freeze2$RecruitmentYear)

#nested for loop for the calculations
rd.bayTitle <- unique(rd.freeze2$MAJOR_AREA_CODE)
rd.yearly_change <-  data.frame(matrix(ncol = 3, nrow = 0))
colnames(rd.yearly_change) <- c('Bays', 'Year', 'per_change')

for (i in 1:length(rd.bayTitle)){
  new.rd <- rd.freeze2 %>% 
    filter(MAJOR_AREA_CODE == rd.bayTitle[i]) %>% 
    arrange(RecruitmentYear)
  for (j in 1:(nrow(new.rd)-1)) {
    change.rd <- format(((new.rd$CPUE[j+1]-new.rd$CPUE[j])/new.rd$CPUE[j]) * 100, scientific = F)
    newrow.rd <- data.frame(Bays = rd.bayTitle[i], Year = new.rd$RecruitmentYear[j+1], per_change =change.rd)
    rd.yearly_change <- rbind(rd.yearly_change, newrow.rd)
  }
}


#done


#re-ordering the levels for the bays
rd.yearly_change$Bays <- as.factor(rd.yearly_change$Bays)

levels(rd.yearly_change$Bays)
rd.yearly_change$Bays <- fct_inorder(rd.yearly_change$Bays)
rd.yearly_change$per_change <- as.numeric(rd.yearly_change$per_change)


rd.yearly_change %>%
  ggplot( aes(x=Bays, y=per_change, fill=Bays)) +
    geom_boxplot(outlier.shape = NA, coef=0) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6)  +
    theme_ipsum() + theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle=45, hjust=1)
    ) 

### Adding it to the percent change plot
RE.RD.freeze.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + 
  geom_boxplot(data = rd.yearly_change, aes(x=Bays, y=per_change, fill=Bays), coef=0, outlier.shape = NA) +
   scale_fill_viridis(discrete = TRUE, alpha=0.2) +
    theme_ipsum()+
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "red drum and freeze"
  ) 


```

```{r red drum and hurricane}

## Setting up the data frame, a function and a for loop needed to be made
rd.hur <- finalcheck
rd.hur <- add_column(rd.hur, RecruitmentYear = NA)

my_function <- function(DATE){
  if (DATE > "2007-09-30" & DATE < "2008-06-01"){
    (RecruitmentYear = 'Year 1')
  }else if(DATE > "2008-09-30" & DATE < "2009-06-01"){
    (RecruitmentYear = 'Year 2')
  }else if (DATE > "2009-09-30" & DATE < "2010-06-01"){
    (RecruitmentYear = 'Year 3')
  }else if (DATE > "2010-09-30" & DATE < "2011-06-01"){
    (RecruitmentYear = 'Year 4')
  }else if (DATE > "2011-09-30" & DATE < "2012-06-01"){
    (RecruitmentYear = 'Year 5')
  }else if (DATE > "2012-09-30" & DATE < "2013-06-01"){
    (RecruitmentYear = 'Year 6')
  }else if (DATE > "2013-09-30" & DATE < "2014-06-01"){
    (RecruitmentYear = 'Year 7')
  }else if (DATE > "2014-09-30" & DATE < "2015-06-01"){
    (RecruitmentYear = 'Year 8')
  }else if (DATE > "2015-09-30" & DATE < "2016-06-01"){
    (RecruitmentYear = 'Year 9')
  }else(RecruitmentYear = 'Year 10')
  return(RecruitmentYear)
}

for (i in 1:nrow(rd.hur)){
  DATE <- rd.hur[i, "DATE"]
  rd.hur[i,"RecruitmentYear"] <- my_function(DATE)
}

### Now it can start like the rest of the r chunks
rd.hur2 <- rd.hur %>% 
  group_by(MAJOR_AREA_CODE,RecruitmentYear) %>% 
  summarize(mean(rd_CPUE)) %>% 
  rename("CPUE" = "mean(rd_CPUE)")

rd.hur2$SPECIES <- "Red Drum"

# Re-ordering the years in the factors
rd.hur2$MAJOR_AREA_CODE <- as.character(rd.hur2$MAJOR_AREA_CODE)
rd.hur2$RecruitmentYear <- as.factor(rd.hur2$RecruitmentYear)
rd.hur2$RecruitmentYear <- factor(rd.hur2$RecruitmentYear, levels = c("Year 1", "Year 2", "Year 3", "Year 4", "Year 5", "Year 6", "Year 7", "Year 8", "Year 9", "Year 10"))

levels(rd.hur2$RecruitmentYear)

#nested for loop for the calculations
rdHH.bayTitle <- unique(rd.hur2$MAJOR_AREA_CODE)
rdHH.yearly_change <-  data.frame(matrix(ncol = 3, nrow = 0))
colnames(rdHH.yearly_change) <- c('Bays', 'Year', 'per_change')

for (i in 1:length(rdHH.bayTitle)){
  new.rdHH <- rd.hur2 %>% 
    filter(MAJOR_AREA_CODE == rdHH.bayTitle[i]) %>% 
    arrange(RecruitmentYear)
  for (j in 1:(nrow(new.rdHH)-1)) {
    change.rdHH <- format(((new.rdHH$CPUE[j+1]-new.rdHH$CPUE[j])/new.rdHH$CPUE[j]) * 100, scientific = F)
    newrow.rdHH <- data.frame(Bays = rdHH.bayTitle[i], Year = new.rdHH$RecruitmentYear[j+1], per_change =change.rdHH)
    rdHH.yearly_change <- rbind(rdHH.yearly_change, newrow.rdHH)
  }
}

#done


#re-ordering the levels for the bays
rdHH.yearly_change$Bays <- as.factor(rdHH.yearly_change$Bays)

levels(rdHH.yearly_change$Bays)
rdHH.yearly_change$Bays <- fct_inorder(rdHH.yearly_change$Bays)
rdHH.yearly_change$per_change <- as.numeric(rdHH.yearly_change$per_change)


rdHH.yearly_change %>%
  ggplot( aes(x=Bays, y=per_change, fill=Bays)) +
    geom_boxplot(outlier.shape = NA, coef=0) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6)  +
    theme_ipsum() + theme_classic() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle=45, hjust=1)
    ) 

### Adding it to the percent change plot
RE.RD.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year'), size = 5) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year'), size = 5) + 
  geom_boxplot(data = rdHH.yearly_change, aes(x=Bays, y=per_change, fill=Bays), coef=0, outlier.shape = NA) +
   scale_fill_viridis(discrete = TRUE, alpha=0.2) +
    theme_ipsum()+
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5")) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.04, units = "npc")),
    size = 0.5
  ) + scale_y_continuous(n.breaks = 20 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "red drum and hurricane harvey"
  ) 


```

# Hurricane Figure - FIGURE 3

```{r 4 panel figure code}
grey <- "#D3D3D3"

A.hurr <- RE.RD.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year', shape = 'First Year'), size = 4) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year', shape = 'Second Year'), size = 4) + 
  geom_boxplot(data = rdHH.yearly_change, aes(x=Bays, y=per_change, alpha = 0.1), coef=0, outlier.shape = NA) + scale_fill_manual(values = NA) + guides(alpha = "none") +
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5"),
                                name = "Post Storm",
                                labels = c("First Year", "Second Year")) +
  scale_shape_manual(name = "Post Storm",
                     labels = c("First Year", "Second Year"),
                     values = c(19, 17)) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.03, units = "npc")),
    size = 0.4
  ) + scale_y_continuous(n.breaks = 5 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "Red Drum"
  ) + coord_cartesian(ylim = c(-100,250))

#ggsave("Figure3A.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")

B.hurr <- RE.SST.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year', shape = 'First Year'), size = 4) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year', shape = 'Second Year'), size = 4) + 
  geom_boxplot(data = yearly_change, aes(x=Bays, y=per_change, alpha = 0.1), coef=0, outlier.shape = NA) + scale_fill_manual(values = NA) + guides(alpha="none") +
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5"),
                                name = "Post Storm",
                                labels = c("First Year", "Second Year")) +
  scale_shape_manual(name = "Post Storm",
                     labels = c("First Year", "Second Year"),
                     values = c(19, 17)) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.03, units = "npc")),
    size = 0.4
  ) + scale_y_continuous(n.breaks = 5 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "Spotted Seatrout"
  ) + coord_cartesian(ylim = c(-100,250))

#ggsave("Figure3B.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")

C.hurr <- RE.BD.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year', shape = 'First Year'), size = 4) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year', shape = 'Second Year'), size = 4) + 
  geom_boxplot(data = bdHH.yearly_change, aes(x=Bays, y=per_change, alpha = 0.1), coef=0, outlier.shape = NA) + scale_fill_manual(values = NA) + guides(alpha = "none") +
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5"),
                                name = "Post Storm",
                                labels = c("First Year", "Second Year")) +
  scale_shape_manual(name = "Post Storm",
                     labels = c("First Year", "Second Year"),
                     values = c(19, 17)) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.03, units = "npc")),
    size = 0.4
  ) + scale_y_continuous(n.breaks = 5 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "Black Drum "
  ) + coord_cartesian(ylim = c(-100,500))

#ggsave("Figure3C.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")


D.hurr <- RE.SF.Spread.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year', shape = 'First Year'), size = 4) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year', shape = 'Second Year'), size = 4) + 
  geom_boxplot(data = sfHH.yearly_change, aes(x=Bays, y=per_change, alpha = 0.1), coef=0, outlier.shape = NA) + scale_fill_manual(values = NA) + guides(alpha = "none")+
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5"),
                                name = "Post Storm",
                                labels = c("First Year", "Second Year")) +
  scale_shape_manual(name = "Post Storm",
                     labels = c("First Year", "Second Year"),
                     values = c(19, 17)) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.03, units = "npc")),
    size = 0.4
  ) + scale_y_continuous(n.breaks = 5 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "Southern Flounder"
  ) + coord_cartesian(ylim = c(-150,400))


#ggsave("Figure3D.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")


fig.3 <- ggarrange(A.hurr + rremove("ylab") + rremove("xlab") + rremove("x.text"), B.hurr + rremove("ylab") + rremove("xlab")+ rremove("x.text"), C.hurr + rremove("ylab")+ rremove("xlab"), D.hurr + rremove("ylab")+ rremove("xlab"), labels = c("A","B", "C", "D"), common.legend = TRUE,ncol = 2, nrow = 2, legend = "right") 

fig.3

annotate_figure(fig.3,
                bottom = text_grob("Bay Location", size = 16, hjust = 1),
                left = text_grob("Percent Change (%)", rot = 90, size = 16),
                top = text_grob("Hurricane Harvey", hjust = 2.75, size = 16))




#ggsave("Figure3_corrected.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")


```


#Freeze figure - FIGURE 4 

```{r 4 panel figure for freeze event}

A.freeze <- RE.RD.freeze.PerChange %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year', shape = 'First Year'), size = 4) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year', shape = 'Second Year'), size = 4) + 
  geom_boxplot(data = rd.yearly_change, aes(x=Bays, y=per_change, alpha = 0.1), coef=0, outlier.shape = NA) + scale_fill_manual(values = NA) + guides(alpha = "none") +
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme +scale_color_manual(values = c("#D81B60", "#1E88E5"),
                                name = "Post Storm",
                                labels = c("First Year", "Second Year")) +
  scale_shape_manual(name = "Post Storm",
                     labels = c("First Year", "Second Year"),
                     values = c(19, 17)) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.03, units = "npc")),
    size = 0.4
  ) + scale_y_continuous(n.breaks = 5 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "Red Drum"
  )+ coord_cartesian(ylim = c(-100,300))
  
#ggsave("Figure4A.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")

B.freeze <- RE.SST.PerChange.freeze %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year', shape = 'First Year'), size = 4) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year', shape = 'Second Year'), size = 4) + 
  geom_boxplot(data = sp.yearly_change, aes(x=Bays, y=per_change, alpha = 0.1), coef=0, outlier.shape = NA) + scale_fill_manual(values = NA) + guides(alpha = "none") +
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5"),
                                name = "Post Storm",
                                labels = c("First Year", "Second Year")) +
  scale_shape_manual(name = "Post Storm",
                     labels = c("First Year", "Second Year"),
                     values = c(19, 17)) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.03, units = "npc")),
    size = 0.4
  ) + scale_y_continuous(n.breaks = 5 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "Spotted Seatrout"
  ) + coord_cartesian(ylim = c(-100,300))
  

#ggsave("Figure4B.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white") 

C.freeze <- RE.BD.PerChange.freeze %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year', shape = 'First Year'), size = 4) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year', shape = 'Second Year'), size = 4) + 
  geom_boxplot(data = bd.yearly_change, aes(x=Bays, y=per_change, alpha = 0.1 ), coef=0, outlier.shape = NA) + scale_fill_manual(values = NA) + guides(alpha = "none") +
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5"),
                                name = "Post Storm",
                                labels = c("First Year", "Second Year")) +
  scale_shape_manual(name = "Post Storm",
                     labels = c("First Year", "Second Year"),
                     values = c(19, 17)) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.03, units = "npc")),
    size = 0.4
  ) + scale_y_continuous(n.breaks = 5 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "Black Drum"
  ) + coord_cartesian(ylim = c(-200,1500))
  
#ggsave("Figure4C.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")  
  
D.freeze <- RE.SF.PerChange.freeze %>%
  ggplot() +
  geom_point(aes(x=MAJOR_AREA_CODE, y=first_perChange, color = 'First Year', shape = 'First Year'), size = 5) +
  geom_point(aes(x=MAJOR_AREA_CODE, y = second_perChange, color = 'Second Year', shape = 'Second Year'), size = 5) + 
  geom_boxplot(data = sf.yearly_change, aes(x=Bays, y=per_change, alpha = 0.1), coef=0, outlier.shape = NA) + scale_fill_manual(values = NA) + guides(alpha="none") +
  theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) +
  My_Theme + scale_color_manual(values = c("#D81B60", "#1E88E5"),
                                name = "Post Storm",
                                labels = c("First Year", "Second Year")) +
  scale_shape_manual(name = "Post Storm",
                     labels = c("First Year", "Second Year"),
                     values = c(19, 17)) +
  geom_hline(yintercept = 0) + geom_segment(
    aes(x = MAJOR_AREA_CODE, y = first_perChange, xend = MAJOR_AREA_CODE, yend = second_perChange),
    arrow = arrow(length = unit(0.03, units = "npc")),
    size = 0.4
  ) + scale_y_continuous(n.breaks = 5 ) + labs(
    y = "Percent Change (%)",
    x = "Bay Location",
    colour = "Post Storm",
    title = "Southern Flounder"
  ) + coord_cartesian(ylim = c(-150,1000))
  
#ggsave("Figure4D.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")



fig.4 <- ggarrange(A.freeze+ rremove("ylab") + rremove("xlab") + rremove("x.text"), B.freeze + rremove("ylab") + rremove("xlab") + rremove("x.text"), C.freeze + rremove("ylab")+ rremove("xlab"), D.freeze + rremove("ylab")+ rremove("xlab"), labels = c("A","B", "C", "D"), common.legend = TRUE,ncol = 2, nrow = 2, legend = "right")

fig.4


annotate_figure(fig.4,
                bottom = text_grob("Bay Location", size = 16, hjust = 1),
                left = text_grob("Percent Change (%)", rot = 90, size = 16),
                top = text_grob("2021 Freeze", hjust = 4, size = 16)
                )

#ggsave("Figure4_corrected.jpg", width = 10, height = 8, units = c("in"), dpi = 300, bg = "white")



```


