---
title: "Appendix"
output:
  pdf_document: default
  geometry: margin=1in
  documentclass: article
  word_document: default
  html_document:
    df_print: paged
---

\renewcommand{\thesection}{S\arabic{section}} 

\renewcommand{\thetable}{S\arabic{table}} 

\renewcommand{\thefigure}{S\arabic{figure}}

\setcounter{table}{0}

\setcounter{figure}{0}

\setcounter{section}{0}

\setcounter{page}{1}

# Supplemental Materials for: Assessing the Resistance and Resilience of Recreationally Important Fish Species to Extreme Events in Coastal Texas

### Authors: Ana C. Silverio*, Mariah C. Livernois, Dakus Geeslin, and Easton R. White



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, warning = FALSE, message = FALSE)

## This will be a compilation of the supplementary material 

#Set working directory:
setwd("~/texas_extreme_events")

#Call in bag seines:
bag.seines <- read.csv("~/texas_extreme_events/Clean_TPWD_Data/UpdatedBagSeinesCondensed_CLEAN.csv")

#Packages:
library(tidyverse)
library(lubridate)
library(knitr)
options(digits = 4)
library(ggforce)
library(tidyverse)
library("hrbrthemes")
library(viridis)
library(forcats)
library(ggpubr)
library(kableExtra)
library(magick)
library(webshot2)
library(jtools)
library(huxtable)


#color palette
colorBlindBlack8 <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00","#CC79A7")

#readable dates:
str(bag.seines)
bag.seines$DATE<- as.Date(bag.seines$DATE,
                                        format = "%m/%d/%y")

#adding the names of the bays into the data frame
bag.seines$MAJOR_AREA_CODE <- as.factor(bag.seines$MAJOR_AREA_CODE)

bag.seines <- bag.seines %>%  
  dplyr::mutate(MAJOR_AREA_CODE = recode(MAJOR_AREA_CODE, `1` = 'SabineLake', `2` = 'GalvestonBay', `3` = 'MatagordaBay', `4` = 'SanAntonioBay', `5`= 'AransasBay', `6`='CorpusChristiBay', `7`='UpperLagunaMadre', `8` = 'LowerLagunaMadre', `9`='EastMatagordaBay', `11` = 'CedarLakes'))

bag.seines <- bag.seines %>% 
  filter(!(MAJOR_AREA_CODE == "CedarLakes")) %>% 
  filter(!(MAJOR_AREA_CODE == "EastMatagordaBay"))

##Plot
My_Theme <- theme(
  axis.title.x = element_text(size = 12),
  axis.text.x = element_text(size = 12),
  axis.title.y = element_text(size = 12),
  plot.title = element_text(size = 12),
  legend.text = element_text(size = 12),
  legend.title = element_text(size = 12),
  axis.ticks.length = unit(0.20, "cm"),
  axis.text.y = element_text(size = 12))



```

```{r time series Monthly Analysis Calculations, include=FALSE}
#calculate monthly averages:
#adding the names of the bays into the data frame
bag.seines$MAJOR_AREA_CODE <- as.factor(bag.seines$MAJOR_AREA_CODE)

#bag.seines <- bag.seines %>% 
  #filter(!(MAJOR_AREA_CODE == "CedarLakes")) %>% 
  #filter(!(MAJOR_AREA_CODE == "EastMatagordaBay"))

## Red drum Monthly Average Calculations -----
redDrum_mon_avg <- bag.seines %>%
  group_by(MONTH,YEAR,MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE))

redDrum_mon_avg <- redDrum_mon_avg %>%
  rename("CPUE_AvgRD" = "mean(rd_CPUE)")


# making column that combines month and year
redDrum_mon_avg$DAY <- 1
redDrum_mon_avg$MDY <- paste(redDrum_mon_avg$MONTH,redDrum_mon_avg$DAY, redDrum_mon_avg$YEAR, sep = "-")
redDrum_mon_avg$MDY <- as.Date(redDrum_mon_avg$MDY, format = "%m-%d-%Y")


## Spotted seatrout Calculation ------
sst_mon_avg <- bag.seines %>%
  group_by(MONTH,YEAR,MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE))

sst_mon_avg <- sst_mon_avg %>%
  rename("CPUE_AvgSST" = "mean(sst_CPUE)")

#sst_mon_avg$MAJOR_AREA_CODE <- as.character(sst_mon_avg$MAJOR_AREA_CODE)

#creating a data column for easier interpretation 
sst_mon_avg$DAY <- 1
sst_mon_avg$MDY <- paste(sst_mon_avg$MONTH,sst_mon_avg$DAY, sst_mon_avg$YEAR, sep = "-")
sst_mon_avg$MDY <- as.Date(sst_mon_avg$MDY, format = "%m-%d-%Y")



#Black drum calculation ---- 
blackDrum_mon_avg <- bag.seines %>%
  group_by(MONTH,YEAR,MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE))

blackDrum_mon_avg  <- blackDrum_mon_avg  %>%
  rename("CPUE_AvgBD" = "mean(bd_CPUE)")

blackDrum_mon_avg$MAJOR_AREA_CODE <- as.character(blackDrum_mon_avg$MAJOR_AREA_CODE)

## creating a data column
blackDrum_mon_avg$DAY <- 1
blackDrum_mon_avg$MDY <- paste(blackDrum_mon_avg$MONTH,blackDrum_mon_avg$DAY, blackDrum_mon_avg$YEAR, sep = "-")
blackDrum_mon_avg$MDY <- as.Date(blackDrum_mon_avg$MDY, format = "%m-%d-%Y")


## Southern Flounder calculation ----

SF_mon_avg <- bag.seines %>%
  group_by(MONTH,YEAR,MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE))

SF_mon_avg  <- SF_mon_avg %>%
  rename("CPUE_AvgSF" = "mean(sf_CPUE)")

SF_mon_avg$MAJOR_AREA_CODE <- as.character(SF_mon_avg$MAJOR_AREA_CODE)

#Creating a data column for easier plot interpretation
SF_mon_avg$DAY <- 1
SF_mon_avg$MDY <- paste(SF_mon_avg$MONTH,SF_mon_avg$DAY, SF_mon_avg$YEAR, sep = "-")
SF_mon_avg$MDY <- as.Date(SF_mon_avg$MDY, format = "%m-%d-%Y")




```


# Time series analysis plots 



```{r Red drum time series plots, parsed out by bay , echo=FALSE, fig.cap= "Red Drum monthly averaged CPUE over the last ten years parsed out by bay system. Dotted lines signifing two extreme events, Hurricane Harvey and the 2021 Texas Freeze, left to right."}

## red drum plot
ggplot(data = redDrum_mon_avg %>% filter(YEAR > 2012), mapping = aes(x = MDY, y =  CPUE_AvgRD)) + geom_line(alpha = 0.8, size = 1) +  
geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000") + 
geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size=1, color = "#000000") +
theme_classic() + facet_wrap(~MAJOR_AREA_CODE, scales = "free") +
   scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  labs(
  title = "Red Drum CPUE Monthly Average Since 2013",
  x = "Time",
  y = "CPUE (#/hectare)" 
) + theme(axis.text.x = element_text(angle=45, hjust=1))


```

```{r spotted seatrout time series plots, parsed out by bay , echo=FALSE, fig.cap= "Spotted Seatrout monthly averaged CPUE over the last ten years parsed out by bay system. Dotted lines signifing two extreme events, Hurricane Harvey and the 2021 Texas Freeze, left to right."}

#spotted seatrout plot
ggplot(data = sst_mon_avg %>% filter(YEAR > 2012), mapping = aes(x = MDY, y =  CPUE_AvgSST)) + geom_line(alpha = 0.8, size = 1) + theme_classic() + facet_wrap(~MAJOR_AREA_CODE, scale = "free") +  
  geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000")+
  geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size = 1, color = "#000000") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  labs(
    title = "Spotted Seatrout CPUE Monthly Average since 2013",
    x = "Time",
    y = "CPUE (#/hectare)"
  )+ theme(axis.text.x = element_text(angle=45, hjust=1)) 
```


```{r black drum time series plots, parsed out by bay , echo=FALSE, fig.cap= "Black Drum monthly averaged CPUE over the last ten years parsed out by bay system. Dotted lines signifing two extreme events, Hurricane Harvey and the 2021 Texas Freeze, left to right."}
## black drum plot
ggplot(data = blackDrum_mon_avg  %>% filter(YEAR > 2012), mapping = aes(x = MDY, y =  CPUE_AvgBD)) + geom_line(alpha = 0.8, size = 1) + theme_classic() + facet_wrap(~MAJOR_AREA_CODE, scale = "free") +  
  geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000")+
  geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size = 1, color = "#000000") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
 labs(
  title = "Black Drum CPUE Monthly Average since 2013",
  x = "Time",
  y = "CPUE (#/hectare)"
) + theme(axis.text.x = element_text(angle=45, hjust=1))

```


```{r Southern Flounder time series plots, parsed out by bay , echo=FALSE, fig.cap= "Southern Flounder monthly averaged CPUE over the last ten years parsed out by bay system. Dotted lines signifing two extreme events, Hurricane Harvey and the 2021 Texas Freeze, left to right."}
## southern flounder plot
ggplot(data = SF_mon_avg %>% filter(YEAR > 2012), mapping = aes(x = MDY, y =  CPUE_AvgSF)) + geom_line(alpha = 0.8, size = 1) + theme_classic() + facet_wrap(~MAJOR_AREA_CODE, scale = "free") +  
  geom_vline(xintercept = as.numeric(as.Date("2017-08-01")), linetype=4, size = 1, color = "#000000")+
  geom_vline(xintercept = as.numeric(as.Date("2021-02-01")), linetype=4, size = 1, color = "#000000") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  labs(
  title = "Southern Flounder CPUE Monthly Average since 2013",
  x = "Time",
  y = "CPUE (#/hectare)"
) + theme(axis.text.x = element_text(angle=45, hjust=1))

```

\newpage

# Recruitment Windows

```{r red drum recruitment window, fig.cap= "Red Drum CPUE monthly average raw data points plots over julian day establishing the recruitment window for Red Drum." }
###Plotting the raw data points starts here####
#plot
ggplot(data = bag.seines %>% filter(YEAR > 2012 & YEAR < 2024), mapping = aes(x = as.Date(JULIAN_DATE, origin = as.Date("2021-01-01")), y = rd_CPUE, group=as.factor(YEAR), color = as.factor(YEAR))) + geom_point() + #geom_smooth() +
  theme_classic() + #facet_wrap(~MAJOR_AREA_CODE) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  labs(
    title = "Red Drum CPUE Monthly Average Since 2013",
    x = "Time",
    y = "CPUE (#/hectare)",
    color = "Year"
  )

```

```{r SST recruitment window, fig.cap= "Spotted Seatrout CPUE monthly average raw data points plots over julian day establishing the recruitment window for Spotted Seatrout." }

ggplot(data = bag.seines %>% filter(YEAR > 2012 & YEAR < 2024), mapping = aes(x = as.Date(JULIAN_DATE, origin = as.Date("2021-01-01")), y = (sst_CPUE), group=as.factor(YEAR), color = as.factor(YEAR))) + geom_point() + #geom_smooth() +
  theme_classic() + #facet_wrap(~MAJOR_AREA_CODE) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  labs(
    title = "SST CPUE Monthly Average Since 2013",
    x = "Time",
    y = "CPUE (#/hectare)",
     color = "Year"
  )
```


```{r Black Drum recruitment window, fig.cap= "Black Drum CPUE monthly average raw data points plots over julian day establishing the recruitment window for Black Drum."}

ggplot(data = bag.seines %>% filter(YEAR > 2012 & YEAR < 2024), mapping = aes(x = as.Date(JULIAN_DATE, origin = as.Date("2021-01-01")), y = bd_CPUE, group=as.factor(YEAR), color = as.factor(YEAR))) + geom_point() + #geom_smooth() +
  theme_classic() + #facet_wrap(~MAJOR_AREA_CODE) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  labs(
    title = "Black Drum CPUE Monthly Average Since 2013",
    x = "Time",
    y = "CPUE (#/hectare)",
     color = "Year"
  ) + ylim(0,4000)


```

```{r SF recruitment window, fig.cap= "Southern Flounder CPUE monthly average raw data points plots over julian day establishing the recruitment window for Southern Flounder."}

ggplot(data = bag.seines %>% filter(YEAR > 2012 & YEAR < 2024), mapping = aes(x = as.Date(JULIAN_DATE, origin = as.Date("2021-01-01")), y = sf_CPUE, group=as.factor(YEAR), color = as.factor(YEAR))) + geom_point() + #geom_smooth() +
  theme_classic() + #facet_wrap(~MAJOR_AREA_CODE) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  labs(
    title = "Southern Flounder CPUE Monthly Average Since 2013",
    x = "Time",
    y = "CPUE (#/hectare)",
     color = "Year"
  )


```

\newpage


# Hurricane Harvey Percent Change Tables

```{r Red Drum Hurricane}
#I had to first subset into the 10 year frame I wanted (no averaging)
check2 <- bag.seines %>%
  filter(YEAR > 2006 & YEAR < 2018 ) %>% 
  group_by(MAJOR_AREA_CODE)

#Then I had to subset for only the months I wanted for red drum (oct - end of may)
check3 <- check2 %>% 
  filter(MONTH < 6 ) %>% 
  group_by(MAJOR_AREA_CODE)

check4 <- check2 %>% 
  filter(MONTH > 9) %>% 
  group_by(MAJOR_AREA_CODE)
#pasting them together
finalcheck <- rbind(check3, check4)

## I realized that the data set has data from an incomplete recruitment window since it starts with 2007 in jan (this recruitment window would have started in oct of the previous year) so I need to make sure it starts in oct of 2007 and ends may of 2016 for the averages
 
finalcheck <- finalcheck %>% 
  filter(DATE > "2007-09-30") %>% 
  filter(DATE < "2017-06-01")


#ggplot(finalcheck, mapping = aes(x=JULIAN_DATE, y = rd_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.RD10yr.hurricane <- finalcheck %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(rd_CPUE)) %>% 
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD10yr.hurricane$SPECIES <- "Red Drum"
RE.RD10yr.hurricane$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.RD1yr.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2017-10-01'), as.Date('2018-05-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE)) %>%
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD1yr.hurricane$SPECIES <- "Red Drum"
RE.RD1yr.hurricane$AVERAGE <- "1st year"


RE.RD2nd.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2018-10-01'), as.Date('2019-05-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE)) %>%
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD2nd.hurricane$SPECIES <- "Red Drum"
RE.RD2nd.hurricane$AVERAGE <- "2nd year"

RE.RDbyyear.Hurr <- rbind(RE.RD10yr.hurricane,RE.RD1yr.hurricane,RE.RD2nd.hurricane)


#Plotting
#ggplot(data = RE.RDbyyear.Hurr , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  #title = "10 yr avg vs post storm avg for RD across bays using NEW baselines",
  #x = "Major bays",
 # y = "Catch per Unit Effort (#/hectare)"
#) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.RD.Spread.PerChange <- spread(RE.RDbyyear.Hurr, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.RD.Spread.PerChange$first_perChange <- NA
RE.RD.Spread.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.RD.Spread.PerChange)){
  RE.RD.Spread.PerChange$first_perChange[i] = format(((RE.RD.Spread.PerChange$`1st year`[i] - RE.RD.Spread.PerChange$`10 yrs`[i]) /RE.RD.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.RD.Spread.PerChange)){
  RE.RD.Spread.PerChange$second_perChange[i] = format(((RE.RD.Spread.PerChange$`2nd year`[i] - RE.RD.Spread.PerChange$`10 yrs`[i]) /RE.RD.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}
```


```{r HH Red Drum Percent Change Table}

#table <- RE.RD.Spread.PerChange
#table <- table %>%  rename(
 #"Bays" = "MAJOR_AREA_CODE"
#)

kable(RE.RD.Spread.PerChange, "latex", booktabs = T, caption = "Red Drum percent changes after Hurricane Harvey") %>% 
  kable_styling(latex_options = c("HOLD_position","scale_down"), full_width = F)

```

```{r Spotted Seatrout Hurricane}
#I had to first subset into the 10 year frame I wanted (no averaging)
subset5 <- bag.seines %>%
  filter(YEAR > 2006 & YEAR < 2017 ) %>% 
  group_by(MAJOR_AREA_CODE)

#Then I had to subset for only the months I wanted for spotted seatrout (june - end of december)
subset6 <- subset5 %>% 
  filter(MONTH > 5 ) %>% 
  group_by(MAJOR_AREA_CODE)

#ggplot(subset6, mapping = aes(x=JULIAN_DATE, y = sst_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.SST10yr.hurricane <- subset6 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(sst_CPUE)) %>% 
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST10yr.hurricane$SPECIES <- "Spotted Seatrout"
RE.SST10yr.hurricane$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.SST1yr.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2018-06-01'), as.Date('2018-12-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE)) %>%
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST1yr.hurricane$SPECIES <- "Spotted Seatrout"
RE.SST1yr.hurricane$AVERAGE <- "1st year"


RE.SST2nd.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2019-06-01'), as.Date('2019-12-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE)) %>%
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST2nd.hurricane$SPECIES <- "Spotted Seatrout"
RE.SST2nd.hurricane$AVERAGE <- "2nd year"

RE.SSTbyyear.Hurr <- rbind(RE.SST10yr.hurricane,RE.SST1yr.hurricane,RE.SST2nd.hurricane)


#Plotting
#ggplot(data = RE.SSTbyyear.Hurr , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  #title = "10 yr avg vs post storm avg for SST across bays using NEW baselines",
  #x = "Major bays",
  #y = "Catch per Unit Effort (#/hectare)"
#) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

## PERCENT CHANGES
#make it wide:
RE.SST.Spread.PerChange <- spread(RE.SSTbyyear.Hurr, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.SST.Spread.PerChange$first_perChange <- NA
RE.SST.Spread.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.SST.Spread.PerChange)){
  RE.SST.Spread.PerChange$first_perChange[i] = format(((RE.SST.Spread.PerChange$`1st year`[i] - RE.SST.Spread.PerChange$`10 yrs`[i]) /RE.SST.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.SST.Spread.PerChange)){
  RE.SST.Spread.PerChange$second_perChange[i] = format(((RE.SST.Spread.PerChange$`2nd year`[i] - RE.SST.Spread.PerChange$`10 yrs`[i]) /RE.SST.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

```

```{r HH and Spotted Seatrout Table}

kable(RE.SST.Spread.PerChange, "latex", booktabs = T, caption = "Spotted Seatrout percent changes after Hurricane Harvey") %>% 
  kable_styling(latex_options = c("HOLD_position","scale_down"), full_width = F)

```

```{r Black Drum and Hurricane}
## Recruitment window is April to end of oct 
#I had to first subset into the 10 year frame I wanted (no averaging)
subset9 <- bag.seines %>%
  filter(YEAR > 2006 & YEAR < 2017 ) %>% 
  group_by(MAJOR_AREA_CODE)


#Then I had to subset for only the months I wanted for black drum (April to end of oct)
subset10 <- subset9 %>% 
  filter(MONTH > 3 & MONTH < 11 ) %>% 
  group_by(MAJOR_AREA_CODE)

#ggplot(subset10, mapping = aes(x=JULIAN_DATE, y = bd_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.BD10yr.hurricane <- subset10 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(bd_CPUE)) %>% 
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD10yr.hurricane$SPECIES <- "Black Drum"
RE.BD10yr.hurricane$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.BD1yr.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2018-04-01'), as.Date('2018-10-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE)) %>%
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD1yr.hurricane$SPECIES <- "Black Drum"
RE.BD1yr.hurricane$AVERAGE <- "1st year"


RE.BD2nd.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2019-04-01'), as.Date('2019-10-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE)) %>%
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD2nd.hurricane$SPECIES <- "Black Drum"
RE.BD2nd.hurricane$AVERAGE <- "2nd year"

RE.BDbyyear.Hurr <- rbind(RE.BD10yr.hurricane,RE.BD1yr.hurricane,RE.BD2nd.hurricane)


#Plotting
#ggplot(data = RE.BDbyyear.Hurr , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  #title = "10 yr avg vs post storm avg for BD across bays using NEW baselines",
  #x = "Major bays",
  #y = "Catch per Unit Effort (#/hectare)"
#) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

## PERCENT CHANGES
#make it wide:
RE.BD.Spread.PerChange <- spread(RE.BDbyyear.Hurr, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.BD.Spread.PerChange$first_perChange <- NA
RE.BD.Spread.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.BD.Spread.PerChange)){
  RE.BD.Spread.PerChange$first_perChange[i] = format(((RE.BD.Spread.PerChange$`1st year`[i] - RE.BD.Spread.PerChange$`10 yrs`[i]) /RE.BD.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.BD.Spread.PerChange)){
  RE.BD.Spread.PerChange$second_perChange[i] = format(((RE.BD.Spread.PerChange$`2nd year`[i] - RE.BD.Spread.PerChange$`10 yrs`[i]) /RE.BD.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

```

```{r HH Black Drum Table}
kable(RE.BD.Spread.PerChange, "latex", booktabs = T, caption = "Black Drum percent changes after Hurricane Harvey") %>% 
  kable_styling(latex_options = c("HOLD_position","scale_down"), full_width = F)

```

```{r Southern Flounder and Hurricane}
## Recruitment window is feb to end of july

#I had to first subset into the 10 year frame I wanted (no averaging)
subset13 <- bag.seines %>%
  filter(YEAR > 2006 & YEAR < 2017 ) %>% 
  group_by(MAJOR_AREA_CODE)


#Then I had to subset for only the months I wanted for southern flounder (feb - end of july)
subset14 <- subset13 %>% 
  filter(MONTH > 1 & MONTH < 8 ) %>% 
  group_by(MAJOR_AREA_CODE)

#ggplot(subset14, mapping = aes(x=JULIAN_DATE, y = sf_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.SF10yr.hurricane <- subset14 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(sf_CPUE)) %>% 
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF10yr.hurricane$SPECIES <- "Southern Flounder"
RE.SF10yr.hurricane$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.SF1yr.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2018-02-01'), as.Date('2018-07-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE)) %>%
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF1yr.hurricane$SPECIES <- "Southern Flounder"
RE.SF1yr.hurricane$AVERAGE <- "1st year"


RE.SF2nd.hurricane <- bag.seines %>%
  filter(between(DATE, as.Date('2019-02-01'), as.Date('2019-07-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE)) %>%
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF2nd.hurricane$SPECIES <- "Southern Flounder"
RE.SF2nd.hurricane$AVERAGE <- "2nd year"

RE.SFbyyear.Hurr <- rbind(RE.SF10yr.hurricane,RE.SF1yr.hurricane,RE.SF2nd.hurricane)


#Plotting
#ggplot(data = RE.SFbyyear.Hurr , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
 # title = "10 yr avg vs post storm avg for SF across bays using NEW baselines",
 # x = "Major bays",
  #y = "Catch per Unit Effort (#/hectare)"
#) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

## PERCENT CHANGES
#make it wide:
RE.SF.Spread.PerChange <- spread(RE.SFbyyear.Hurr, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.SF.Spread.PerChange$first_perChange <- NA
RE.SF.Spread.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.SF.Spread.PerChange)){
  RE.SF.Spread.PerChange$first_perChange[i] = format(((RE.SF.Spread.PerChange$`1st year`[i] - RE.SF.Spread.PerChange$`10 yrs`[i]) /RE.SF.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.SF.Spread.PerChange)){
  RE.SF.Spread.PerChange$second_perChange[i] = format(((RE.SF.Spread.PerChange$`2nd year`[i] - RE.SF.Spread.PerChange$`10 yrs`[i]) /RE.SF.Spread.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

```

```{r HH and Southern Flounder Table, }
kable(RE.SF.Spread.PerChange, "latex", booktabs = T, caption = "Southern Flounder percent changes after Hurricane Harvey") %>% 
  kable_styling(latex_options = c("HOLD_position","scale_down"), full_width = F)
```

\newpage

# Texas 2021 Freeze Percent Change Tables 
```{r Red Drum Feeze}

#I had to first subset into the 10 year frame I wanted (no averaging)
subset2 <- bag.seines %>%
  filter(YEAR > 2008 & YEAR < 2020 ) %>% 
  group_by(MAJOR_AREA_CODE)
#summarize(mean(rd_CPUE)) %>%
#rename("CPUE" = "mean(rd_CPUE)")

#Then I had to subset for only the months I wanted for red drum (oct - end of may)
subset3 <- subset2 %>% 
  filter(MONTH < 6 ) %>% 
  group_by(MAJOR_AREA_CODE)

subset4 <- subset2 %>% 
  filter(MONTH > 9) %>% 
  group_by(MAJOR_AREA_CODE)
#pasting them together
finalsubset <- rbind(subset3, subset4)

## I realized that the data set has data from an incomplete recruitment window since it starts with 2009 in jan (this recruitment window would have started in oct of the previous year) so I need to make sure it starts in oct of 2009 and ends may of 2019 for the averages

finalsubset <- finalsubset %>% 
  filter(DATE > "2009-09-30") %>% 
  filter(DATE < "2019-06-01")


#ggplot(finalsubset, mapping = aes(x=JULIAN_DATE, y = rd_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.RD10yr.freeze <- finalsubset %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(rd_CPUE)) %>% 
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD10yr.freeze$SPECIES <- "Red Drum"
RE.RD10yr.freeze$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.RD1yr.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2021-10-01'), as.Date('2022-05-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE)) %>%
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD1yr.freeze$SPECIES <- "Red Drum"
RE.RD1yr.freeze$AVERAGE <- "1st year"


RE.RD2nd.freeze<- bag.seines %>%
  filter(between(DATE, as.Date('2022-10-01'), as.Date('2023-05-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(rd_CPUE)) %>%
  rename("CPUE" = "mean(rd_CPUE)")

RE.RD2nd.freeze$SPECIES <- "Red Drum"
RE.RD2nd.freeze$AVERAGE <- "2nd year"

RE.RDbyyear.Freeze <- rbind(RE.RD10yr.freeze,RE.RD1yr.freeze,RE.RD2nd.freeze)


#Plotting
#ggplot(data = RE.RDbyyear.Freeze , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
  #title = "10 yr avg vs post freeze avg for RD across bays using NEW baselines",
 # x = "Major bays",
 # y = "Catch per Unit Effort (#/hectare)"
#) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.RD.freeze.PerChange <- spread(RE.RDbyyear.Freeze, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.RD.freeze.PerChange$first_perChange <- NA
RE.RD.freeze.PerChange$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.RD.freeze.PerChange)){
  RE.RD.freeze.PerChange$first_perChange[i] = format(((RE.RD.freeze.PerChange$`1st year`[i] - RE.RD.freeze.PerChange$`10 yrs`[i]) /RE.RD.freeze.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.RD.freeze.PerChange)){
  RE.RD.freeze.PerChange$second_perChange[i] = format(((RE.RD.freeze.PerChange$`2nd year`[i] - RE.RD.freeze.PerChange$`10 yrs`[i]) /RE.RD.freeze.PerChange$`10 yrs`[i]) * 100 , scientific = F)
}


```

```{r Freeze Red Drum Table}

kable(RE.RD.freeze.PerChange, "latex", booktabs = T, caption = "Red Drum percent changes after freeze event") %>% 
  kable_styling(latex_options = "HOLD_position", full_width = F)

```

```{r Spotted Seatrout and Texas Freeze}

# Spotted seatrout freeze baseline
#I had to first subset into the 10 year frame I wanted (no averaging)
subset7 <- bag.seines %>%
  filter(YEAR > 2009 & YEAR < 2020 ) %>% 
  group_by(MAJOR_AREA_CODE)
#summarize(mean(rd_CPUE)) %>%
#rename("CPUE" = "mean(rd_CPUE)")

#Then I had to subset for only the months I wanted for spotted seatrout (june - end of dec)
subset8 <- subset7 %>% 
  filter(MONTH > 5 ) %>% 
  group_by(MAJOR_AREA_CODE)

#ggplot(subset8, mapping = aes(x=JULIAN_DATE, y = sst_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.SST10yr.freeze <- subset8 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(sst_CPUE)) %>% 
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST10yr.freeze$SPECIES <- "Spotted Seatrout"
RE.SST10yr.freeze$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.SST1yr.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2021-06-01'), as.Date('2021-12-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE)) %>%
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST1yr.freeze$SPECIES <- "Spotted Seatrout"
RE.SST1yr.freeze$AVERAGE <- "1st year"


RE.SST2nd.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2022-06-01'), as.Date('2022-12-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sst_CPUE)) %>%
  rename("CPUE" = "mean(sst_CPUE)")

RE.SST2nd.freeze$SPECIES <- "Spotted Seatrout"
RE.SST2nd.freeze$AVERAGE <- "2nd year"

RE.SSTbyyear.Freeze <- rbind(RE.SST10yr.freeze,RE.SST1yr.freeze,RE.SST2nd.freeze)


#Plotting
#ggplot(data = RE.SSTbyyear.Freeze , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
 # title = "10 yr avg vs post storm avg for SST across bays using NEW baselines",
  #x = "Major bays",
  #y = "Catch per Unit Effort (#/hectare)"
#) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.SST.PerChange.freeze <- spread(RE.SSTbyyear.Freeze, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.SST.PerChange.freeze$first_perChange <- NA
RE.SST.PerChange.freeze$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.SST.PerChange.freeze)){
  RE.SST.PerChange.freeze$first_perChange[i] = format(((RE.SST.PerChange.freeze$`1st year`[i] - RE.SST.PerChange.freeze$`10 yrs`[i]) /RE.SST.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.SST.PerChange.freeze)){
  RE.SST.PerChange.freeze$second_perChange[i] = format(((RE.SST.PerChange.freeze$`2nd year`[i] - RE.SST.PerChange.freeze$`10 yrs`[i]) /RE.SST.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

```

```{r Freeze and Spotted Seatrout Table}
kable(RE.SST.PerChange.freeze, "latex", booktabs = T, caption = "Spotted Seatrout percent changes after freeze event") %>% 
  kable_styling(latex_options = c("HOLD_position", "scale_down"), full_width = F)

```

```{r Black Drum and Texas Freeze}

# black drum freeze baseline
#I had to first subset into the 10 year frame I wanted (no averaging)
subset11 <- bag.seines %>%
  filter(YEAR > 2009 & YEAR < 2020 ) %>% 
  group_by(MAJOR_AREA_CODE)

#Then I had to subset for only the months I wanted for black drum (April - end of oct)
subset12 <- subset11 %>% 
  filter(MONTH > 3 & MONTH < 11 ) %>% 
  group_by(MAJOR_AREA_CODE)

#ggplot(subset12, mapping = aes(x=JULIAN_DATE, y = bd_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.BD10yr.freeze <- subset12 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(bd_CPUE)) %>% 
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD10yr.freeze$SPECIES <- "Black Drum"
RE.BD10yr.freeze$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.BD1yr.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2021-04-01'), as.Date('2021-10-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE)) %>%
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD1yr.freeze$SPECIES <- "Black Drum"
RE.BD1yr.freeze$AVERAGE <- "1st year"


RE.BD2nd.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2022-04-01'), as.Date('2022-10-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(bd_CPUE)) %>%
  rename("CPUE" = "mean(bd_CPUE)")

RE.BD2nd.freeze$SPECIES <- "Black Drum"
RE.BD2nd.freeze$AVERAGE <- "2nd year"

RE.BDbyyear.Freeze <- rbind(RE.BD10yr.freeze,RE.BD1yr.freeze,RE.BD2nd.freeze)


#Plotting
#ggplot(data = RE.BDbyyear.Freeze , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
 # title = "10 yr avg vs post storm avg for BD across bays using NEW baselines",
  #x = "Major bays",
  #y = "Catch per Unit Effort (#/hectare)"
#) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.BD.PerChange.freeze <- spread(RE.BDbyyear.Freeze, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.BD.PerChange.freeze$first_perChange <- NA
RE.BD.PerChange.freeze$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.BD.PerChange.freeze)){
  RE.BD.PerChange.freeze$first_perChange[i] = format(((RE.BD.PerChange.freeze$`1st year`[i] - RE.BD.PerChange.freeze$`10 yrs`[i]) /RE.BD.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.BD.PerChange.freeze)){
  RE.BD.PerChange.freeze$second_perChange[i] = format(((RE.BD.PerChange.freeze$`2nd year`[i] - RE.BD.PerChange.freeze$`10 yrs`[i]) /RE.BD.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}



```

```{r Freeze and Black Drum Table}

kable(RE.BD.PerChange.freeze, "latex", booktabs = T, caption = "Black Drum percent changes after freeze event") %>% 
  kable_styling(latex_options = c("HOLD_position","scale_down"), full_width = F)

```

```{r Southern Flounder and Texas Freeze}

# southern flounder freeze baseline
#I had to first subset into the 10 year frame I wanted (no averaging)
subset15 <- bag.seines %>%
  filter(YEAR > 2009 & YEAR < 2020 ) %>% 
  group_by(MAJOR_AREA_CODE)

#Then I had to subset for only the months I wanted for southern flounder feb -end of july
subset16 <- subset15 %>% 
  filter(MONTH > 1 & MONTH < 8 ) %>% 
  group_by(MAJOR_AREA_CODE)

#ggplot(subset16, mapping = aes(x=JULIAN_DATE, y = sf_CPUE)) + geom_point() + theme_classic()

#Final step = Averaging for the baseline
RE.SF10yr.freeze <- subset16 %>% 
  group_by(MAJOR_AREA_CODE) %>% 
  summarize(mean(sf_CPUE)) %>% 
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF10yr.freeze$SPECIES <- "Southern Flounder"
RE.SF10yr.freeze$AVERAGE <- "10 yrs"

## post storm calculations = 2 post storm recruitment windows
RE.SF1yr.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2021-02-22'), as.Date('2021-07-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE)) %>%
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF1yr.freeze$SPECIES <- "Southern Flounder"
RE.SF1yr.freeze$AVERAGE <- "1st year"


RE.SF2nd.freeze <- bag.seines %>%
  filter(between(DATE, as.Date('2022-02-22'), as.Date('2022-07-31'))) %>% 
  group_by(MAJOR_AREA_CODE) %>%
  summarize(mean(sf_CPUE)) %>%
  rename("CPUE" = "mean(sf_CPUE)")

RE.SF2nd.freeze$SPECIES <- "Southern Flounder"
RE.SF2nd.freeze$AVERAGE <- "2nd year"

RE.SFbyyear.Freeze <- rbind(RE.SF10yr.freeze,RE.SF1yr.freeze,RE.SF2nd.freeze)


#Plotting
#ggplot(data = RE.SFbyyear.Freeze , mapping = aes(x = MAJOR_AREA_CODE, y =  CPUE, fill = AVERAGE)) +  geom_bar(stat="identity", color="black", position=position_dodge()) + scale_fill_grey() + theme_classic() + labs(
 # title = "10 yr avg vs post storm avg for SF across bays using NEW baselines",
  #x = "Major bays",
  #y = "Catch per Unit Effort (#/hectare)"
#) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


## PERCENT CHANGES
#make it wide:
RE.SF.PerChange.freeze <- spread(RE.SFbyyear.Freeze, AVERAGE, CPUE)

## Add the column to put in the percent change values
RE.SF.PerChange.freeze$first_perChange <- NA
RE.SF.PerChange.freeze$second_perChange <- NA

# for loop calculating per change for the first year
for (i in 1:nrow(RE.SF.PerChange.freeze)){
  RE.SF.PerChange.freeze$first_perChange[i] = format(((RE.SF.PerChange.freeze$`1st year`[i] - RE.SF.PerChange.freeze$`10 yrs`[i]) /RE.SF.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}

#for loop for calculating per change for the 2nd year to the baseline = 
for (i in 1:nrow(RE.SF.PerChange.freeze)){
  RE.SF.PerChange.freeze$second_perChange[i] = format(((RE.SF.PerChange.freeze$`2nd year`[i] - RE.SF.PerChange.freeze$`10 yrs`[i]) /RE.SF.PerChange.freeze$`10 yrs`[i]) * 100 , scientific = F)
}


```

```{r Freeze and Southern Flounder Table}
kable(RE.SF.PerChange.freeze, "latex", booktabs = T, caption = "Southern Flounder percent changes after freeze event") %>% 
  kable_styling(latex_options = c("HOLD_position","scale_down"), full_width = F)

```

